---
title: "Curriculum Vitae"
# title: "&nbsp;"
author: "Emilio M. Bruna"
email: embruna@ufl.edu
web: www.BrunaLab.org
github: embruna
twitter: BrunaLab
phone: "(352) 514-3935"
date: "`r format(Sys.time(), '%B %Y')`"
geometry: margin=1in
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
# tables: true
# jobtitle: "Professor & Distinguished Teaching Scholar, University of Florida"
# address: "PO Box 110430 · 110 Newins-Ziegler Hall · Gainesville, FL 32611-040"
fontawesome: yes
# bibliography: BrunaPublications.bib
bibliography: ./cv_files/BrunaPublications.bib
# bibliography_software: chapters.bib
# csl: biotropica.csl
csl: ./cv_files/brunacv2.csl
updated: yes
# site: bookdown::bookdown_site
header-includes:
- \usepackage{etaremune} #for reverse-numbered list
- \usepackage[default]{sourcesanspro}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \fancyfoot[R]{`r format(Sys.time(), '%B %Y')`}
- \fancyhead[R]{Emilio M. Bruna, p. \thepage}
- \usepackage{setspace}
- \usepackage{parskip} 
- \usepackage{xcolor} 
- \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  # to center to top level (#) headings - my name 
  # more info # https://www.ctan.org/pkg/sectsty
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
- \usepackage{sectsty} \subsubsectionfont{\color{darkmidnightblue}}
# http://latexcolor.com/ to choose colors
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}

# - \setstretch{1.0}
# https://babichmorrowc.github.io/post/changing-fonts-in-rmarkdown-pdfs/

output:
   pdf_document: default
   html_document:
   df_print: paged
   toc: false
# 
# 
# 
#    # \printbibliography[type=book,title={Books only}]
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(citr)
library(RefManageR)
```
<!-- this next line suppresses the header (line, name,  page number) on 1st page -->
\thispagestyle{empty}  
# EMILIO MIGUEL BRUNA
\vspace{-0.3cm}  
University of Florida\hfill embruna@ufl.edu  
Dept. of Wildlife Ecology & Conservation &\hfill +1 (352) 846-0634  
Center for Latin American Studies\hfill&nbsp;[www.brunalab.org](www.brunalab.org)  
Gainesville, FL 32611-0430 USA\hfill&nbsp;[\@BrunaLab](https://twitter.com/BrunaLab) 
\vspace{-01cm}  
<!-- ___   -->
\par\noindent\rule{\textwidth}{0.4pt}
\textbf{\textcolor{darkmidnightblue}{RESEARCH \& TEACHING INTERESTS:}} Tropical ecology and conservation, plant population ecology, plant-animal interactions, scientometrics and bibliometrics, science & science policy in Latin America  

\textbf{\textcolor{darkmidnightblue}{LANGUAGES:}} Native fluency in Spanish and English, Fluent in Portuguese  
\vspace{-0.6cm}  

### EDUCATION
\begingroup 
\setlength{\leftskip}{.2cm} 

2001\hspace{4mm} Ph.D. in Population Biology, University of California, Davis  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm}  _Dissertation Co-Advisors: Susan P. Harrison and Sharon Y. Strauss_   -->
1995\hspace{4mm} M.S. in Biology, University of California, San Diego  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm} _Thesis Advisor: Ted J. Case_   -->
1994\hspace{4mm} B.S. in Ecology, Behavior, & Evolution with a minor in Literature, University of California, San Diego  

\endgroup 

<!-- ```{r ed, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- ed<-read_csv("./cv_files/education.csv") %>% -->
<!-- replace_na(list(program=" ", school=" ",year=" ",degree=" ")) -->
<!-- ed$program<-gsub('","',", ",ed$program) -->
<!-- ed$school<-gsub('","',", ",ed$school) -->
<!-- kbl(ed, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->

<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # row_spec(0:0, bold = T) %>% -->
<!--   # # column_spec(2, width = "35em") %>% -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->
<!-- ``` -->

### PROFESSIONAL APPOINTMENTS
\begingroup 
\setlength{\leftskip}{.2cm} 

2013-Present\hspace{6mm}**Professor & Distinguished Teaching Scholar**, University of Florida  
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2012-Present\hspace{6mm}**Director**, Florida-Brazil Linkage Institute, University of Florida   
&nbsp;\hspace{24mm}Center for Latin American Studies, University of Florida  

2020-2021\hspace{10mm}**President**, Association for Tropical Biology and Conservation  

2013-2019\hspace{10mm}**Editor-in-Chief**, _Biotropica_  

2014-2020\hspace{10mm}**Board of Directors**, Dryad Digital Data Repository  

2007-2013\hspace{10mm}**Associate Professor**, University of Florida  
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2002-2007\hspace{10mm}**Assistant Professor**, University of Florida    
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2001-2002\hspace{10mm}**NSF Minority Postdoctoral Fellow**, Biological Dynamics of Forest Fragments Project  
&nbsp;\hspace{24mm}Instituto Nacional de Pesquisas da Amazônia-Smithsonian Institution  

\endgroup

<!-- ```{r positions, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- positions<-read_csv("./cv_files/positions.csv") %>% -->
<!-- replace_na(list(dates=" ", position=" ")) -->

<!-- # positions<-as.data.frame(positions) -->
<!-- # positions[1,1] <- cell_spec(positions[1, 1], "latex", bold = T)  -->
<!-- kbl(positions, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->

<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # row_spec(0:0, bold = T) %>% -->
<!--   # # column_spec(2, width = "35em") %>% -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->
<!-- ``` -->


### AWARDS

<!-- ```{r awards, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- awards<-read_csv("./cv_files/fellowships.csv") %>%  -->
<!--   filter(cat=="award") %>%  -->
<!--   select(-cat) %>%  -->
<!--   arrange(desc(year)) -->
<!-- awards$prize<-gsub('","',",",awards$prize) -->
<!-- awards$prize<-gsub("for the","\nfor the",awards$prize) -->
<!-- # awards$prize<- linebreak(awards$prize,double_escape = F, linebreaker = "\\n") -->
<!-- kbl(awards, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->
<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # column_spec(2, width = "35em") %>%  -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->

<!-- ``` -->

\begingroup 
\setlength{\leftskip}{.2cm}  
2020\hspace{4mm}Selected for Induction into Alpha Zeta (Faculty Affiliate, UF Chapter)    
2020\hspace{4mm}Roche Teaching Scholar, UF College of Agricultural and Life Sciences    
2016\hspace{4mm}Sigma Xi (Full Member, University of Florida Chapter)    
2014\hspace{4mm}Academy of Distinguished Teaching Scholars, University of Florida  
2012\hspace{4mm}Outstanding Paper Award, US Chapter of the International Association for Landscape Ecology  
2011\hspace{4mm}Graduate Advisor & Teacher of the Year, UF College of Agricultural and Life Sciences  
2009\hspace{4mm}University of Florida Research Foundation Professor  
2007\hspace{4mm}Julie S. Denslow Outstanding Article Prize, _Biotropica_ & the Association for Tropical Biology & Conservation  
2005\hspace{4mm}UF International Educator of the Year (untenured faculty category)  
2003\hspace{4mm}Diversity Scholar, American Institute for Biological Sciences  
2002\hspace{4mm}John L. Harper Early Career Researcher Award, British Ecological Society  
1994\hspace{4mm}Ernest C. Mort Leadership Excellence Award, Revelle College, UC San Diego  
<!-- &nbsp;\quad\quad\quad\quad _for the year’s outstanding contribution to the field, published in any journal_   -->
<!-- &nbsp;\quad\quad\quad\quad _for the outstanding paper published in the journal Biotropica_   -->
<!-- &nbsp;\quad\quad\quad\quad _for the outstanding paper by a young investigator in the Journal of Ecology_ -->

\endgroup

### FELLOWSHIPS
<!-- # ```{r fellowships, echo=FALSE,message = FALSE,warning=FALSE} -->
<!-- #  -->
<!-- # fellowships<-read_csv("./cv_files/fellowships.csv") %>% filter(cat=="fellowship") %>% select(-cat) -->
<!-- # kbl(fellowships,digits = 1, -->
<!-- #                   format = "latex", -->
<!-- #                   align="l", -->
<!-- #     col.names = NULL, -->
<!-- #     longtable = T, -->
<!-- #                   row.names = FALSE, -->
<!-- #                   booktabs=T, -->
<!-- #                   linesep = "") %>% -->
<!-- #   kable_styling(bootstrap_options = c("hover"), -->
<!-- #                 latex_options = c("scale_down"), -->
<!-- #                 full_width = F, -->
<!-- #                 font_size = 10, -->
<!-- #                 position = "left") %>% -->
<!-- #   sub("\\\\toprule", "", .) %>% -->
<!-- #   sub("\\\\bottomrule", "", .) -->
<!-- #  -->
<!-- # ``` -->

\begingroup 
\setlength{\leftskip}{.2cm}  

2012\hspace{4mm}*Ciência Sem Fronteiras* Special Visiting Researcher Fellowship, CNPq Brazil  
2009\hspace{4mm}Fulbright Scholar, Brazil  
2009\hspace{4mm}Visiting Researcher Fellowship, CNPq Brazil  
2001\hspace{4mm}NSF Minority Postdoctoral Research Fellowship  
2001\hspace{4mm}NSF International Research Fellowship *(declined)*  
2000\hspace{4mm}Ford Foundation Dissertation Year Fellowship  
1999\hspace{4mm}UC Davis Graduate Studies Fellowship  
1998\hspace{4mm}UC Davis John F. Steindler Graduate Fellowship  
1995\hspace{4mm}NSF Minority Predoctoral Research Fellowship  
1993\hspace{4mm}Howard Hughes Senior Honors Thesis Fellowship  
1993\hspace{4mm}UCSD Howard Hughes Summer Research Fellowship  

\endgroup

### RECENT GRANTS IN SUPPORT OF RESEARCH, TRAINING, & PROGRAM DEVELOPMENT (total >$5.5 million)  

\begingroup 
\setlength{\leftskip}{.2cm}  

1. Sloan Foundation. “Reinventing Field Courses” ($74,060; PI: E. M. Bruna, Co-PIs: R. McCleery, P. Antonenko, N. Attias, D. Barton, 2020-2021)

2. National Science Foundation. SG: Synergistic effects of forest fragmentation and droughts on tropical plant population dynamics ($199,904; PI: E. M. Bruna, Co-PIs: M. Uriarte, 2020-2022).

2. National Science Foundation. REU Supplement for "SG: Synergistic effects of forest fragmentation and droughts on tropical plant population dynamics ($14,400; PI: E. M. Bruna, Co-PIs: M. Uriarte, 2021).

3. National Science Foundation. “The role of the matrix in fragmented landscapes: experimental tests and novel theory ($525,000; PI: R. Fletcher, Co-PIs: E. M. Bruna, R. D. Holt, and B. Reichert, 2018-2023)  

4. UF Informatics Institute SEED Funds: “Cross-National Patterns of Productivity & Collaboration by Latin American Scientists” ($20,000, PI: E. M. Bruna, Co-PIs: Stephen Perz, Chris McCarty).

5. Mindlin Foundation. “Who are the Gatekeepers of Discovery? A crowdsourced project to ID & map the editors of academic journals” ($3633, 2017-2018).

\endgroup

<!-- ### GRANT PROPOSALS UNDER REVIEW or IN PREPARATION -->


<!-- --- -->
<!-- nocite: '@*' -->
<!-- ... -->

### RECENT PEER-REVIEWED PUBLICATIONS, BOOK CHAPTERS, & ESSAYS (Total N = 105)

<!-- this allows you to print text after the "References" section -->
<!-- <div id="refs"></div>  -->

<!-- maybe to print out by reference groups? -->
<!-- https://forums.zotero.org/discussion/23604/a-mini-guide-to-sort-bibliography-by-reference-type -->
<!-- \endgroup  -->
1. Mundim, F. M. E. H. M. Vieira-Neto, H. Alborn, & E. M. Bruna. *In press*. Disentangling the influence of resource variability and simultaneous attacks on whole-plant tolerance to herbivory. *Journal of Ecology* [PhD Thesis Chapter].  

1. Bruna, E.M., R Chazdon, TM Errington and BA Nosek. 2021. A proposal to advance theory and promote collaboration in tropical biology by supporting replications. _Biotropica_, 53: 6-10.  

1. Barbosa Silva, LV, HL Vasconcelos, MC Mack, AdS Ferreira, and EM Bruna. 2020. Effects of experimental nitrogen enrichment on soil properties and litter decomposition in a Neotropical savanna. _Austral Ecology_ 45:1093-1102. [Ph. D. Thesis Chapter].  

7. Brooks, ME, K Kristensen, MR Darrigo, P Rubim, M Uriarte, E Bruna, and BM Bolker. 2019. Statistical modeling of patterns in annual reproductive rates. _Ecology_ 100 (7):e02706 [Ph.D. Thesis Chapter].  

10. Bruna, EM 2018. Editorial board members are a non-random sample of ecological experts. _Nature Ecology and Evolution_ 2(2):202.  


### SOFTWARE (N=1)

1. Fournier, A., F. Stevens, M. Boone, and E. M. Bruna. 2020. refsplitr. author name disambiguation, author georeferencing, and mapping of coauthorship networks with Web of Science data. R package version 1.0.0. https://github.com/ropensci/refsplitr



### COURSE DEVELOPMENT & TEACHING AT THE UNIVERSITY OF FLORIDA

\begingroup 
\setlength{\leftskip}{.2cm}  



Ecology and Conservation of Tropical Wildlife (Undergraduate, 03,05,07,11,12,14,18)  
Data Collection & Management for Latin American Studies (Graduate, 2019)  
Plant-Animal Interactions (Graduate, 2004, 2006, 2008, 2010)  
Fundraising for Tropical Conservation & Development (Graduate, 2013, 2016, 2018, 2020)  
Scientific Publishing (Graduate, 2014, 2015, 2017, 2018)  
Ecological Principles for Development & Conservation Professionals (Graduate, 2010, 2011, 2012)  
Tropical Forest Community Ecology (Graduate, 2000)  
Design and Methods of Research in Latin American Studies (Graduate, 2008, 2010)  
Research Methods in Tropical Conservation & Development (Graduate, 2003-2007)  
Seminar in Wildlife Ecology and Conservation (Graduate, 2003, 2004)  
Social Media Workshop (Graduate, 2016)  

\endgroup 

### GRADUATE STUDENTS ADVISED AS COMMITTEE CHAIR
```{r GradStudents, echo=FALSE,message = FALSE,warning=FALSE}

grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="advisor") %>% select(-role)
kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
    col.names = NULL,
    longtable = T,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)

```



Students under my supervision have been awarded over $35,000 in grants to support their research and been the recipients of prestigious fellowships and awards to support their studies: 

*	FLAS Fellowship (S. Parsons)
*	NSF Predoctoral Fellowships (M. Trager, S. Copeland)
*	UF IGERT Fellowship (C. Lucas)
*	Inter-American Foundation Grassroots Development Fellowship (C. Lucas)
*	UF Alumni Fellowship (M. Trager)
*	Fulbright Fellowship (A. Neto)
*	Science Without Borders Doctoral Fellowship (E. V. Neto, F. Mundim).
*	NSF Doctoral Dissertation Enhancement Grant (C. Lucas)
*	UF-WEC Jennings Scholarship (A. Neto, M. Trager, F. Mundim, G. Iacona) 
*	UF-CALS Doris Lowe & Earl & Verna Lowe Scholarship (C. Lucas, E. V. Neto). 

Research by my students has also been recognized for its excellence: 

*	Fabiane Mundim: 2016 UF-WEC High-Impact Publication
*	Ana Cecilia Silva: Honorable Mention, 2015 Charles Wood Thesis Award, UF Latin American Studies
*	Fabiane Mundim: Honorable Mention, 2012 OTS Outstanding Paper Competition 
*	Christine Lucas: 2012 Marianne Schmink Award for the University of Florida’s outstanding Dissertation in Tropical Conservation and Development.
*	Ernane Vieira Neto: 2011 E. Lucy Braun Award (Outstanding poster presented at the Annual Meeting of the Ecological Society of America).
*	Matthew Trager: 2005 Wildlife Grad Student Assoc. Outstanding Research Award (MS Category).

