---
title: "Curriculum Vitae"
# title: "&nbsp;"
author: "Emilio M. Bruna"
email: embruna@ufl.edu
web: www.BrunaLab.org
github: embruna
twitter: BrunaLab
phone: "(352) 514-3935"
date: "`r format(Sys.time(), '%B %Y')`"
geometry: margin=1in
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
# tables: true
# jobtitle: "Professor & Distinguished Teaching Scholar, University of Florida"
# address: "PO Box 110430 · 110 Newins-Ziegler Hall · Gainesville, FL 32611-040"
fontawesome: yes
# bibliography: BrunaPublications.bib
bibliography: ./cv_files/BrunaPublications.bib
# bibliography_software: chapters.bib
# csl: biotropica.csl
csl: ./cv_files/brunacv2.csl
updated: yes
# site: bookdown::bookdown_site
header-includes:
- \usepackage{etaremune} # for reverse-numbered list of publications etc
- \usepackage[default]{sourcesanspro}
- \usepackage{fancyhdr} # modify header into left, center, right
- \pagestyle{fancy} # cues the use of fancy headers
- \fancyfoot{} # cues the use of fancy footer
- \fancyfoot[R]{`r format(Sys.time(), '%B %Y')`} # month & year on footer right
- \fancyhead[R]{Emilio M. Bruna, p. \thepage} # name and page on header right
- \usepackage{setspace} # manipulate line spacing 
- \usepackage{parskip} # manipulate indents and spacing before/after paragraphs 
- \usepackage{xcolor} # changes colors of text
- \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  # to center to top level (#) headings (my name) and change color of font
  # more info # https://www.ctan.org/pkg/sectsty
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
# to center to sub-sub-headings (###) and change color of font
- \usepackage{sectsty} \subsubsectionfont{\color{darkmidnightblue}}
# http://latexcolor.com/ to choose colors
# define the colors used above with rgb codes
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}

# - \setstretch{1.0}
# https://babichmorrowc.github.io/post/changing-fonts-in-rmarkdown-pdfs/

output:
   pdf_document: default
   html_document:
   df_print: paged
   toc: false
# 
# 
# 
#    # \printbibliography[type=book,title={Books only}]
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
# library(citr)
library(RefManageR)
```
<!-- this next line suppresses the header (line, name,  page number) on 1st page -->
\thispagestyle{empty}  
# EMILIO MIGUEL BRUNA
\vspace{-0.3cm}  <!--space between name and address -->
University of Florida\hfill embruna@ufl.edu  
Dept. of Wildlife Ecology & Conservation &\hfill +1 (352) 846-0634  
Center for Latin American Studies\hfill&nbsp;[www.brunalab.org](www.brunalab.org)  
Gainesville, FL 32611-0430 USA\hfill&nbsp;[\@BrunaLab](https://twitter.com/BrunaLab) 
\vspace{-0.5cm}  <!--there was too much space, so reduced it with minus: -Xcm -->
<!-- ___   -->
\par\noindent\rule{\textwidth}{0.4pt}
\textbf{\textcolor{darkmidnightblue}{RESEARCH \& TEACHING INTERESTS:}} Tropical ecology and conservation, plant population ecology, plant-animal interactions, scientometrics and bibliometrics, science & science policy in Latin America  

\textbf{\textcolor{darkmidnightblue}{LANGUAGES:}} Native fluency in Spanish and English, Fluent in Portuguese  
\vspace{-0.6cm}  

### EDUCATION
<!--to indent a block of stuff treat it as a 'group' and then set leftskip -->
<!--be sure to indicate where the group ends with \endgroup -->

\begingroup 
\setlength{\leftskip}{.2cm} 

2001\hspace{4mm} Ph.D. in Population Biology, University of California, Davis  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm}  _Dissertation Co-Advisors: Susan P. Harrison and Sharon Y. Strauss_   -->
1995\hspace{4mm} M.S. in Biology, University of California, San Diego  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm} _Thesis Advisor: Ted J. Case_   -->
1994\hspace{4mm} B.S. in Ecology, Behavior, & Evolution with a minor in Literature, University of California, San Diego  

\endgroup 

<!-- ```{r ed, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- ed<-read_csv("./cv_files/education.csv") %>% -->
<!-- replace_na(list(program=" ", school=" ",year=" ",degree=" ")) -->
<!-- ed$program<-gsub('","',", ",ed$program) -->
<!-- ed$school<-gsub('","',", ",ed$school) -->
<!-- kbl(ed, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->

<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # row_spec(0:0, bold = T) %>% -->
<!--   # # column_spec(2, width = "35em") %>% -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->
<!-- ``` -->

### PROFESSIONAL APPOINTMENTS
\begingroup 
\setlength{\leftskip}{.2cm} 

2013-Present\hspace{6mm}**Professor & Distinguished Teaching Scholar**, University of Florida  
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2020-2021\hspace{10mm}**President**, Association for Tropical Biology and Conservation  

2012-2021\hspace{10mm}**Director**, Florida-Brazil Linkage Institute, University of Florida   
&nbsp;\hspace{24mm}Center for Latin American Studies, University of Florida  

2013-2019\hspace{10mm}**Editor-in-Chief**, _Biotropica_  

2014-2020\hspace{10mm}**Board of Directors**, Dryad Digital Data Repository  

2005-Present\hspace{6mm}**Adjunct Professor**, Universidade Federal de Uberlândia, Brazil  
&nbsp;\hspace{24mm}Graduate Program in Ecology and Natural Resource Conservation  

2007-2013\hspace{10mm}**Associate Professor**, University of Florida  
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2002-2007\hspace{10mm}**Assistant Professor**, University of Florida    
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2001-2002\hspace{10mm}**NSF Minority Postdoctoral Fellow**, Biological Dynamics of Forest Fragments Project  
&nbsp;\hspace{24mm}Instituto Nacional de Pesquisas da Amazônia-Smithsonian Institution  

\endgroup

<!-- ```{r positions, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- positions<-read_csv("./cv_files/positions.csv") %>% -->
<!-- replace_na(list(dates=" ", position=" ")) -->

<!-- # positions<-as.data.frame(positions) -->
<!-- # positions[1,1] <- cell_spec(positions[1, 1], "latex", bold = T)  -->
<!-- kbl(positions, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->

<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # row_spec(0:0, bold = T) %>% -->
<!--   # # column_spec(2, width = "35em") %>% -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->
<!-- ``` -->


### AWARDS

<!-- ```{r awards, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- awards<-read_csv("./cv_files/fellowships.csv") %>%  -->
<!--   filter(cat=="award") %>%  -->
<!--   select(-cat) %>%  -->
<!--   arrange(desc(year)) -->
<!-- awards$prize<-gsub('","',",",awards$prize) -->
<!-- awards$prize<-gsub("for the","\nfor the",awards$prize) -->
<!-- # awards$prize<- linebreak(awards$prize,double_escape = F, linebreaker = "\\n") -->
<!-- kbl(awards, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->
<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # column_spec(2, width = "35em") %>%  -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->

<!-- ``` -->

\begingroup 
\setlength{\leftskip}{.2cm}  
2020\hspace{4mm}Selected for Induction into Alpha Zeta (Faculty Affiliate, UF Chapter)    
2020\hspace{4mm}Roche Teaching Scholar, UF College of Agricultural and Life Sciences    
2016\hspace{4mm}Sigma Xi (Full Member, University of Florida Chapter)    
2014\hspace{4mm}Academy of Distinguished Teaching Scholars, University of Florida  
2012\hspace{4mm}Outstanding Paper Award, US Chapter of the International Association for Landscape Ecology  
2011\hspace{4mm}Graduate Advisor & Teacher of the Year, UF College of Agricultural and Life Sciences  
2009\hspace{4mm}University of Florida Research Foundation Professor  
2007\hspace{4mm}Julie S. Denslow Outstanding Article in _Biotropica_ Prize, Association for Tropical Biology & Conservation  
2005\hspace{4mm}UF International Educator of the Year (untenured faculty category)  
2003\hspace{4mm}Diversity Scholar, American Institute for Biological Sciences  
2002\hspace{4mm}John L. Harper Early Career Researcher Award, British Ecological Society  
1994\hspace{4mm}Ernest C. Mort Leadership Excellence Award, Revelle College, UC San Diego  
<!-- &nbsp;\quad\quad\quad\quad _for the year’s outstanding contribution to the field, published in any journal_   -->
<!-- &nbsp;\quad\quad\quad\quad _for the outstanding paper published in the journal Biotropica_   -->
<!-- &nbsp;\quad\quad\quad\quad _for the outstanding paper by a young investigator in the Journal of Ecology_ -->

\endgroup

### FELLOWSHIPS
<!-- # ```{r fellowships, echo=FALSE,message = FALSE,warning=FALSE} -->
<!-- #  -->
<!-- # fellowships<-read_csv("./cv_files/fellowships.csv") %>% filter(cat=="fellowship") %>% select(-cat) -->
<!-- # kbl(fellowships,digits = 1, -->
<!-- #                   format = "latex", -->
<!-- #                   align="l", -->
<!-- #     col.names = NULL, -->
<!-- #     longtable = T, -->
<!-- #                   row.names = FALSE, -->
<!-- #                   booktabs=T, -->
<!-- #                   linesep = "") %>% -->
<!-- #   kable_styling(bootstrap_options = c("hover"), -->
<!-- #                 latex_options = c("scale_down"), -->
<!-- #                 full_width = F, -->
<!-- #                 font_size = 10, -->
<!-- #                 position = "left") %>% -->
<!-- #   sub("\\\\toprule", "", .) %>% -->
<!-- #   sub("\\\\bottomrule", "", .) -->
<!-- #  -->
<!-- # ``` -->

\begingroup 
\setlength{\leftskip}{.2cm}  

2012\hspace{4mm}*Ciência Sem Fronteiras* Special Visiting Researcher Fellowship, CNPq Brazil  
2009\hspace{4mm}Fulbright Scholar, Brazil  
2009\hspace{4mm}Visiting Researcher Fellowship, CNPq Brazil  
2001\hspace{4mm}NSF Minority Postdoctoral Research Fellowship  
2001\hspace{4mm}NSF International Research Fellowship *(declined)*  
2000\hspace{4mm}Ford Foundation Dissertation Year Fellowship  
1999\hspace{4mm}UC Davis Graduate Studies Fellowship  
1998\hspace{4mm}UC Davis John F. Steindler Graduate Fellowship  
1995\hspace{4mm}NSF Minority Predoctoral Research Fellowship  
1993\hspace{4mm}Howard Hughes Senior Honors Thesis Fellowship  
1993\hspace{4mm}UCSD Howard Hughes Summer Research Fellowship  

\endgroup

### GRANTS IN SUPPORT OF RESEARCH, TRAINING, & PROGRAM DEVELOPMENT (>$5.5 million)  

\begingroup 
\setlength{\leftskip}{.2cm}  

1. Sloan Foundation. “Reinventing Field Courses” ($74,060; PI: E. M. Bruna, Co-PIs: R. McCleery, P. Antonenko, N. Attias, D. Barton, 2020-2021)

2. National Science Foundation. SG: Synergistic effects of forest fragmentation and droughts on tropical plant population dynamics ($199,904; PI: E. M. Bruna, Co-PIs: M. Uriarte, 2020-2022).

2. National Science Foundation. REU Supplement for "SG: Synergistic effects of forest fragmentation and droughts on tropical plant population dynamics ($14,400; PI: E. M. Bruna, Co-PIs: M. Uriarte, 2021).

3. National Science Foundation. “The role of the matrix in fragmented landscapes: experimental tests and novel theory ($548,058; PI: R. Fletcher, Co-PIs: E. M. Bruna, R. D. Holt, and B. Reichert, 2018-2023)  

4. UF Informatics Institute SEED Funds: “Cross-National Patterns of Productivity & Collaboration by Latin American Scientists” ($20,000, PI: E. M. Bruna, Co-PIs: Stephen Perz, Chris McCarty).

5. Mindlin Foundation. “Who are the Gatekeepers of Discovery? A crowdsourced project to ID & map the editors of academic journals” ($3633, 2017-2018).

5. National Geographic Global Exploration Fund. “Experimental climate change in the Amazon: How will rising CO2 influence plants, insects, and their interactions?” ($19,970, PI: E. M. Bruna, Co-PIs H. Vasconcelos, F. Mundim, D. Lapola).

5. John Wiley and Sons. “Funds to support the Biotropica Editorial Office” ($199,945; 2014-2019).

5. UF Center for Latin American Studies Faculty Travel Award ($1500)

5. UF Center for Latin American Studies Speakers Program. “Herton Escobar: Science Correspondent, Estado de São Paulo Newspaper ($2000, including matching funds provided by the College of Journalism and Communications, the Tropical Conservation and Development Program, and Office of the VP for Research).

5. UF Center for Latin American Studies Faculty Research Award: “Cross-national patterns of productivity and collaboration by Latin American ecologists” ($5450, 2012-2013).

5. National Science Foundation: “Doctoral Dissertation Enhancement Proposal: International: Carbon sequestration and tree biodiversity in Amazonian floodplain forests”.  ($11,000; OISE-0929183 to E. Bruna prepared by and for doctoral student Christine Lucas, 2010-2012).

5. David and Lucile Packard Foundation. “Nitrogen dynamics in Brazil’s Cerrado” ($142,198, Grant 2008-32691 to E. Bruna and co-PIs M. Mack and H. Vasconcelos, 2009-2011).

5. National Science Foundation. “IGERT in Spatial Ecology & Evolution: Quantitative Training in Biology, Statistics, & Mathematics”. ($2,958,113; PI: B. Bolker; Co-PI’s: E. Bruna, C. Osenberg, M. Martcheva, & M. Christman, 2008-2013).

5. UF International Center. “International Speakers Program: Dr. Claudio Padua, 2008 UF Distinguished Alumnus” ($1500, with $3500 in matching funds from Wildlife Ecology and Conservation, Latin American Studies, the Tropical Conservation and Development Program, and Institute for Agricultural and Life Sciences).

5. US Department of Education Fund for the Improvement of Postsecondary Education (FIPSE). “Energy, environment, and sustainable development: the central role of the United States and Brazil” ($202,329; PI: J. Kahn, Washington & Lee University; E. Bruna is UF Project Director; 2006-2010)

5. National Science Foundation Collaborative Grant.  “Mechanisms influencing seedling recruitment and establishment in a fragmented Amazonian landscape” DEB-0614149 to E. Bruna ($230,888) and DEB-0614339 to M. Uriarte, Columbia Univ. ($251,831; 2006-10).

5. National Science Foundation Minority Career Advancement Award. “Linking population and ecosystem ecology: how does nitrogen deposition influence plant demography in tropical savannas?”  DEB-0542287 ($174,499; 2006-08).

5. Joseph Jones Ecological Research Center. “Productivity and Biodiversity Patterns: Control in a SE Coastal Plain Landscape (Support for the graduate studies of Gwen Iacona)”. ($19,860; 2005-2007).

5. National Science Foundation Collaborative Grant. “Elucidating mechanisms of coexistence in a community of ant-plant mutualists”.  DEB-0453631 to E. Bruna ($245,096) & DEB-0452720 to B. Inouye, FSU ($260,000; 2005-09).

5. National Science Foundation Grant OISE-0437369.  “U.S.-Brazil Collaborative Research: Seed predation and herbivory in Neotropical savannas: are there demographic consequences for plants?” ($25,012; 2005-2008).

5.  Nacional de Desenvolvimento Científico e Tecnológico, Brazil. “Top-down effects on the structure of Cerrado plant communities” (R$ 22,875.74, Co-PI, 2005-2007)

5. Fundação de Amparo a Pesquisa do Estado de Minas Gerais, Brazil. “Diversity and conservation of invertebrates in the ‘Triângulo Mineiro’: a case study using ants as bioindicators” (R$12,924.13; Senior Collaborator, 2005-2007)

5. Fundação de Amparo a Pesquisa do Estado de Minas Gerais, Brazil (Fapemig). “Effect of herbivory by leaf-cutter ants on Cerrado vegetation” (R$25,229.74, Co-PI, 2004-2006)

5. School for Natural Resources and the Environment New Faculty Support Program. “Seed predation and herbivory in Neotropical savannas: are there demographic consequences for plants?” ($5,000; 2004)

5. Alfred P. Sloan Foundation.  “Increasing the number of minority Ph.D.’s studying Ecology at UF.” ($32,440 and four-year Teaching Assistantships from the College of Agricultural and Life Sciences; 2004).

5. National Science Foundation Research Starter Grant DEB-0309819.  “The effect of forest fragmentation on ant-plant mutualisms.” $50,585; 2003-2005).

5. USAID Subcontract from IIEB.  “Sustainable Communities and Landscapes: A proposed 	program to sustain natural ecosystems and enhance local livelihoods in Brazil’s Amazon and Atlantic Forest regions” ($199,145; 10/01/03-9/30/07; PI: Marianne Schmink; EB and 5 other Co-PIs).

5. Instituto Internacional de Educação do Brasil-SUNY International Development Group.  “Training of young scientists in Amazonia: A new internship program at the Biological Dynamics of Forest Fragments Project.” (R$21,000; co-PI Patricia Delamônica, 2001).

5. National Science Foundation Minority Postdoctoral Research Fellowship DBI-0109226. “The effect of forest fragmentation on ant-plant mutualisms” ($190,200; 2001).

5. NSF Dissertation Improvement Grant INT 98-06351. “Effect of habitat fragmentation on the growth, reproduction, and population dynamics of an Amazonian understory herb” ($17,600; 1998-2000).

5. Grants for Graduate Research: Smithsonian Institution, Manomet Observatory Kathleen S. Anderson Award, Wilson Ornithological Society Paul A. Stewart Award, and UC Davis (M.E. Mathias Award, Graduate Studies Research Grant, Jastro-Shields Research Award, and Center for Population Biology Summer Research Grant (Total: $11860; 1996-1997).

5. Grants for Undergraduate Research: Explorer’s Club Grant, UCSD Undergraduate Scholastic Research Grant (Total: $1955; 1994-1995).

\endgroup

<!-- ### GRANT PROPOSALS UNDER REVIEW or IN PREPARATION -->


<!-- --- -->
<!-- nocite: '@*' -->
<!-- ... -->
### PEER-REVIEWED ARTICLES, SOFTWARE, ESSAYS, AND OTHER PRODUCTS  

*Note: I do not co-author papers from my students’ theses unless I have made contributions substantially beyond the mentoring, fundraising, and editing I consider my fundamental responsibility as their advisor. Moreover, I encourage lab members to engage in side projects, which often result in publications on which I am not a co-author. A list of my lab members’ publications on which I am not a coauthor is below.* 


### MANUSCRIPTS & OTHER PRODUCTS IN REVIEW or REVISION (N=2)

4. Resende Rodrigues, D., Y. R. Bovolenta, E. M. Bruna, J. A. Pimenta, E. Bianchini. Coexistence of understory tree species via architecture differentiation in the Atlantic Forest of southern Brazil. *Plant Ecology.*

3. Halpern, Benjamin S. *et al.* Priorities for synthesis in ecology and environmental science. *Frontiers in Ecology and the Environment *

<!-- this allows you to print text after the "References" section -->
<!-- <div id="refs"></div>  -->

<!-- maybe to print out by reference groups? -->
<!-- https://forums.zotero.org/discussion/23604/a-mini-guide-to-sort-bibliography-by-reference-type -->
<!-- \endgroup  -->


### PEER-REVIEWED PUBLICATIONS, BOOK CHAPTERS, & ESSAYS (N = 107)


1. 	Scott, E. R., M. Uriarte, and E. M. Bruna. *In press.* Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments. *Global Change Biology*. Preprint at [https://doi.org/10.1101/2021.06.28.450186](https://doi.org/10.1101/2021.06.28.450186)

2. Smith, A. C., L. Merz, J. Borden, C. Gulick, A. R. Kshirsagar, and E. M. Bruna. *In press*. Article processing charges, the geographic diversity of author communities, and barriers to publication for authors in the Global South. *Quantitative Science Studies*.  Preprint at [https://doi.org/10.21222/osf.io/s7cx4](https://doi.org/10.21222/osf.io/s7cx4)

1. Mundim, F. M. E. H. M. Vieira-Neto, H. Alborn, & E. M. Bruna. 2021. Disentangling the influence of resource variability and simultaneous attacks on whole-plant tolerance to herbivory. *Journal of Ecology* 109:2729– 2739. [PhD Thesis Chapter].  https://doi.org/10.1111/1365-2745.13684

1. Bruna, E.M., R Chazdon, TM Errington and BA Nosek. 2021. A proposal to advance theory and promote collaboration in tropical biology by supporting replications. _Biotropica_, 53:6-10.  

1. Barbosa Silva, LV, HL Vasconcelos, MC Mack, AdS Ferreira, and EM Bruna. 2020. Effects of experimental nitrogen enrichment on soil properties and litter decomposition in a Neotropical savanna. _Austral Ecology_ 45:1093-1102. [Ph. D. Thesis Chapter].  

2. Fournier, Auriel. Matthew E. Boone, Forrest R. Stevens, and Emilio M. Bruna. 2020. refsplitr: Author name disambiguation, author georeferencing, and mapping of coauthorship networks with Web of
Science data. *Journal of Open Source Software*, 5(45):2028. https://doi.org/10.21105/joss.02028


2. Beckman, NG, CE Aslan, HS Rogers, O Kogan, JL Bronstein, JM Bullock, F Hartig, J HilleRisLambers, Y Zhou, D Zurell, JF Brodie, EM Bruna, RS Cantrell, RR Decker, E Efiom, EC Fricke, K Gurski, A Hastings, JS Johnson, BA Loiselle, MN Miriti, MG Neubert, L Pejchar, JR Poulsen, G Pufal, OH Razafindratsima, ME Sandor, K Shea, S Schreiber, EW Schupp, RS Snell, C Strickland, and J Zambrano. 2020. Advancing an interdisciplinary framework to study seed dispersal ecology. _AoB Plants_ 12:plz048.  

3. Costa, AN, A Bartimachi, HL Vasconcelos, EM Bruna, and EHM Vieira-Neto. 2020. Annual litter production in a Brazilian Cerrado woodland savanna. _Southern Forests_ 82:65-69.  

4. Powers, JS, EM Bruna, A Campos-Arceiz, P Delamonica Sampaio, SJ DeWalt, LG Lohmann, and RA Zahawi. 2020. Tropical biology and conservation in the time of the covid-19 pandemic. _Biotropica_ 52:399-399.  

5. Aslan, C, NG Beckman, HS Rogers, J Bronstein, D Zurell, F Hartig, K Shea, L Pejchar, M Neubert, J Poulsen, J HilleRisLambers, M Miriti, B Loiselle, E Effiom, J Zambrano, G Schupp, G Pufal, J Johnson, JM Bullock, J Brodie, E Bruna, RS Cantrell, R Decker, E Fricke, K Gurski, A Hastings, O Kogan, O Razafindratsima, M Sandor, S Schreiber, R Snell, C Strickland, and Y Zhou. 2019. Employing plant functional groups to advance seed dispersal ecology and conservation. _AoB Plants_ 11:plz006.  

7. Brooks, ME, K Kristensen, MR Darrigo, P Rubim, M Uriarte, E Bruna, and BM Bolker. 2019. Statistical modeling of patterns in annual reproductive rates. _Ecology_ 100 (7):e02706 [Ph.D. Thesis Chapter].  

8. Costa, AN, HL Vasconcelos, EHM Vieira-Neto, and EM Bruna. 2019. Adaptive foraging of leaf-cutter ants to spatiotemporal changes in resource availability in Neotropical savannas. _Ecological Entomology_ 44:227-238.  

9. Fletcher, RJ, Jr., JA Sefair, C Wang, CL Poli, TAH Smith, EM Bruna, RD Holt, M Barfield, AJ Marx, and MA Acevedo. 2019. Towards a unified framework for connectivity that disentangles movement and mortality in space and time. _Ecology Letters_ 22:1680-1689.  

10. Bruna, EM 2018. Editorial board members are a non-random sample of ecological experts. _Nature Ecology and Evolution_ 2(2):202.  

10. Costa, AN, EM Bruna, and HL Vasconcelos. 2018. Do an ecosystem engineer and environmental gradient act independently or in concert to shape juvenile plant communities? Tests with the leaf-cutter ant _Atta laevigata_ in a Neotropical savanna. _PeerJ_ 6:e5612.  [Ph. D. Thesis Chapter].  

11. Brito Darosci, AA, EM Bruna, JC Motta-Junior, CdS Ferreira, JG Blake, and CB Rodrigues Munhoz. 2017. Seasonality, diaspore traits and the structure of plant-frugivore networks in Neotropical savanna forest. _Acta Oecologica_ 84:15-22.  [Ph. D. Thesis Chapter].  

12. Brudvig, LA, SJ Leroux, CH Albert, EM Bruna, KF Davies, RM Ewers, DJ Levey, R Pardini, and J Resasco. 2017. Evaluating conceptual models of landscape change. _Ecography_ 40:74-84.  

13. Costa, AN, HL Vasconcelos, and EM Bruna. 2017. Biotic drivers of seedling establishment in Neotropical savannas: Selective granivory and seedling herbivory by leaf-cutter ants as an ecological filter. _Journal of Ecology_ 105:132-141. [Ph. D. Thesis Chapter].    

14. Espin, J, S Palmas, F Carrasco-Rueda, K Riemer, PE Allen, N Berkebile, KA Hecht, K Kastner-Wilcox, MM Nunez-Regueiro, C Prince, C Rios, E Ross, B Sangha, T Tyler, J Ungvari-Martin, M Villegas, TT Cataldo, and EM Bruna. 2017. A persistent lack of international representation on editorial boards in environmental biology. _Plos Biology_ 15:e2002760.  

15. Mundim, FM, HT Alborn, EHM Vieira-Neto, and EM Bruna. 2017. A whole-plant perspective reveals unexpected impacts of above- and belowground herbivores on plant growth and defense. _Ecology_ 98:70-78.  

16. Resasco, J, EM Bruna, NM Haddad, C Banks-Leite, and CR Margules. 2017. The contribution of theory and experiments to conservation in fragmented landscapes. _Ecography_ 40:109-118.  

17. Rocha-Ortega, M, A Bartimachi, J Neves, EM Bruna, and HL Vasconcelos. 2017. Seed removal patterns of pioneer trees in an agricultural landscape. _Plant Ecology_ 218:737-748.   

16.	Pitman, N. C. A., J. Widmer, E. M. Bruna, C. N. Jenkins, G. Stocks, L. Seales, F. Paniagua, and E. Maehr. 2017. El sorprendente liderazgo del Ecuador en la producción científica de la región andino-amazónica, pp. 27-30 in D. Romo et al. (eds.), Los Secretos del Yasuní: Avances en investigación en la Estación de Biodiversidad Tiputini, Universidad San Francisco de Quito, Quito.  

18. Carvalho, KS, MAF Carneiro, IC Nascimento, AK Saha, and EM Bruna. 2016. Lower ant diversity on earth mounds in a semi-arid brazilian ecosystem: Natural or a sign of degradation? _Sociobiology_ 63(4):1022-1030.    

19. Mundim, FM, and EM Bruna. 2016. Is there a temperate bias in our understanding of how climate change will alter plant- herbivore interactions? A meta- analysis of experimental studies. _American Naturalist_ 188:S74-S89. [Ph. D. Thesis Chapter] **[2016 UF-WEC “High Impact Publication”]**.  

20. Sobrinho, MS, M Tabarelli, IC Machado, JC Sfair, EM Bruna, and AV Lopes. 2016. Land use, fallow period and the recovery of a caatinga forest. _Biotropica_ 48:586-597.    

21. Vieira-Neto, EHM, HL Vasconcelos, and EM Bruna. 2016. Roads increase population growth rates of a native leaf-cutter ant in Neotropical savannahs. _Journal of Applied Ecology_ 53:983-992. [Ph. D. Thesis Chapter].  

7.	Parker, TH, Nakagawa, S, Gurevitch, J and IIEE (Improving Inference in Evolutionary Biology and Ecology) workshop participants. 2016. Promoting transparency in evolutionary biology and ecology. *Ecology Letters*, 19: 726–728.   

9.	Whitlock, MC, JL Bronstein, EM Bruna, AM Ellison, CW Fox, MA McPeek, AJ Moore, MAF Noor, MD Rausher, LH Rieseberg, M G Ritchie, and RG Shaw. 2016. A balanced data archiving policy for long-term studies. *Trends in Ecology and Evolution* 31(2) 84-85 [Response to article].  

10. Fine, P.V.A. and Bruna, E.M. 2016. Neotropical White-sand Forests: Origins, Ecology and Conservation of a Unique Rain Forest Environment. *Biotropica*, 48: 5-6. https://doi.org/10.1111/btp.12305

21.	Hoeksema, JD and EM Bruna. 2015. Context-dependent outcomes of mutualistic interactions. Pages 181-202 in Mutualism, JL Bronstein (ed.). Oxford University Press. 

22. Bruna, EM, TJ Izzo, BD Inouye, and HL Vasconcelos. 2014. Effect of mutualist partner identity on plant demography. _Ecology_ 95:3237-3243. [Cover Article].  

23. Cho, AH, SA Johnson, CE Schuman, JM Adler, O Gonzalez, SJ Graves, JR Huebner, DB Marchant, SW Rifai, I Skinner, and EM Bruna. 2014. Women are underrepresented on the editorial boards of journals in environmental biology and natural resource management. _PeerJ_ 2:e542. **[Named to the 2015 _PeerJ_ Picks Collection (Highlighting 20 articles of the 471 published in 2014)]**.   

24. Smith, MJ, C Weinberger, EM Bruna, and S Allesina. 2014. The scientific impact of nations: Journal placement and citation performance. _PLoS ONE_ 9:e109195.  

25. Braunger Vasconcelos, P, GM Araújo, and EM Bruna. 2014. The role of roadsides in conserving cerrado plant diversity. _Biodiversity and Conservation_ 23:3035-3050.  

14.	V. Christianini, P. S. Oliveira, E. M. Bruna, H. L. Vasconcelos. 2014. Fauna in decline: Meek shall inherit. *Science* 354(6201):1129.  

15.	Bruna, E. M. 2014 On identifying rising stars in biology. *Bioscience.* 64(3):169.  

26. Girão, LC, AV Lopes, M Tabarelli, and EM Bruna. 2014. Mudanças em atributos reprodutivos de árvores reduzem a diversidade funcional em uma paisagem fragmentada de floresta Atlântica pp. 145-174 in Serra Grande: Uma Floresta de ideas.  M. Tabarelli, A. V. Neto, I. R. Leal, and A. V. Lopes (Eds.).  Editora Universitároa da UFPE. Recife. [translation of Girão I 2007, _PLoS ONE_].  

26. Araújo, GM, AF Amaral, EM Bruna, and HL Vasconcelos. 2013. Fire drives the reproductive responses of herbaceous plants in a Neotropical swamp. _Plant Ecology_ 214:1479-1484.  

27. Côrtes, MC, M Uriarte, MR Lemes, R Gribel, W John Kress, PE Smouse, and EM Bruna. 2013. Low plant density enhances gene dispersal in the Amazonian understory herb _Heliconia acuminata_. _Molecular Ecology_ 22:5716-5729. [Ph. D. Thesis Chapter].  

28. Jurinitz, CF, AA de Oliveira, and EM Bruna. 2013. Abiotic and biotic influences on early-stage survival in two shade-tolerant tree species in Brazil's Atlantic forest. _Biotropica_ 45:728-736.  [Ph. D. Thesis Chapter].  

29. Lucas, CM, EM Bruna, and CMN Nascimento. 2013. Seedling co-tolerance of multiple stressors in a disturbed tropical floodplain forest. _Ecosphere_ 4(1):3.  [Ph. D. Thesis Chapter].  

30. Copeland, SM, EM Bruna, LV Barbosa Silva, MC Mack, and HL Vasconcelos. 2012. Short-term effects of elevated precipitation and nitrogen on soil fertility and plant growth in a Neotropical savanna. _Ecosphere_ 3.  [Ph. D. Thesis Chapter].   

31. Iacona, GD, LK Kirkman, and EM Bruna. 2012. Experimental test for facilitation of seedling recruitment by the dominant bunchgrass in a fire-maintained savanna. _PLoS ONE_ 7.  [Ph. D. Thesis Chapter].  

32. Mundim, FM, EM Bruna, EHM Vieira-Neto, and HL Vasconcelos. 2012. Attack frequency and the tolerance to herbivory of Neotropical savanna trees. _Oecologia_ 168:405-414.  [Ph. D. Thesis Chapter].  

33. Passmore, HA, EM Bruna, SM Heredia, and HL Vasconcelos. 2012. Resilient networks of ant-plant mutualists in Amazonian forest fragments. _PLoS ONE_ 7(8):e40803.  

34. Vasconcelos, HL, and EM Bruna. 2012. Arthropod responses to the experimental isolation of Amazonian forest fragments. _Zoologia_ 29:515-530. **[Invited review]**.  

36.	Palumbo, MJ, SA Johnson, FM Mundim, AC Wolf, S Arunachalam, O Gonzalez, A Lau, JL Ulrich, A Washuta, EM Bruna. 2012. Harnessing smartphones for ecological education, research, and outreach.  _Bulletin of the Ecological Society of America_ 93(4): 390-393.  

35. Bruna, EM, and AS de Andrade. 2011. Edge effects on growth and biomass partitioning of an Amazonian understory herb (_Heliconia acuminata_; Heliconiaceae). _American Journal of Botany_ 98:1727-1734.   

36. Bruna, EM, TJ Izzo, BD Inouye, M Uriarte, and HL Vasconcelos. 2011. Asymmetric dispersal and colonization success of Amazonian plant-ants queens. _PLoS ONE_ 6:e22937.  

37. Ferreira, AV, EM Bruna, and HL Vasconcelos. 2011. Seed predators limit plant recruitment in Neotropical savannas. _Oikos_ 120:1013-1022.  

39.	Uriarte, M. Anciães, M. T.B. da Silva, P. Rubim, E. Johnson, and E. M. Bruna.  2011. Disentangling the drivers of reduced long-distance seed dispersal by birds in an experimentally fragmented  landscape.  Ecology 92(4): 924-93. **[2012 Outstanding Paper in Landscape Ecology, Int. Assoc. for Landscape Ecology - US Chapter]**.  

38. Gagnon, PR, EM Bruna, P Rubim, MR Darrigo, RC Littell, M Uriarte, and WJ Kress. 2011. Growth of an understory herb is chronically reduced in Amazonian forest fragments. _Biological Conservation_ 144:830-835.  

39. Laurance, WF, JLC Camargo, RCC Luizao, SG Laurance, SL Pimm, EM Bruna, PC Stouffer, GB Williamson, J Benitez-Malvido, HL Vasconcelos, KS Van Houtan, CE Zartman, SA Boyle, RK Didham, A Andrade, and TE Lovejoy. 2011. The fate of Amazonian forest fragments: A 32-year investigation. _Biological Conservation_ 144:56-67. **[Highlighted as “Exceptional” by the Faculty of 1000]**.  

40. Pitman, NCA, J Widmer, CN Jenkins, G Stocks, L Seales, F Paniagua, and EM Bruna. 2011. Volume and geographical distribution of ecological research in the Andes and the Amazon, 1995-2008. _Tropical Conservation Science _ 4:64-81.    

41. Bruna, EM, JF Guimarães, CT Lopes, R Pacheco, KG Facure, FG Lemos, and HL Vasconcelos. 2010. Mammalia, Estação Ecologica do Panga, a Cerrado protected area in Minas Gerais state, Brazil. _CheckList: Journal of Species Lists and Distribution_ 6:668-675.  

42. Fiske, IJ, and EM Bruna. 2010. Alternative spatial sampling in studies of plant demography: Consequences for estimates of population growth rate. _Plant Ecology_ 207:213-225. [Ph. D. Thesis Chapter].    

43. Fortini, LB, EM Bruna, DJ Zarin, SS Vasconcelos, and IS Miranda. 2010. Altered resource availability and the population dynamics of tree species in Amazonian secondary forests. _Oecologia_ 162:923-934.    

44. Iacona, GD, LK Kirkman, and EM Bruna. 2010. Effects of resource availability on seedling recruitment in a fire-maintained savanna. _Oecologia_ 163:171-180.  [Ph. D. Thesis Chapter].  

45. Quitete Portela, RDC, EM Bruna, and FA Maes dos Santos. 2010. Demography of palm species in Brazil's Atlantic Forest: A comparison of harvested and unharvested species using matrix models. _Biodiversity and Conservation_ 19:2389-2403. [Ph. D. Thesis Chapter].   

46. Quitete Portela, RdC, EM Bruna, and FA Maes dos Santos. 2010. Are protected areas really protecting populations? A test with an Atlantic Rain Forest palm. _Tropical Conservation Science_ 3:361-372.  [Ph. D. Thesis Chapter].  

47. Ribeiro, MBN, EM Bruna, and W Mantovani. 2010. Influence of post-clearing treatment on the recovery of herbaceous plant communities in Amazonian secondary forests. _Restoration Ecology_ 18:50-58.  [Ph. D. Thesis Chapter].  

48. Uriarte, M, EM Bruna, P Rubim, M Anciaes, and I Jonckheere. 2010. Effects of forest fragmentation on the seedling recruitment of a tropical herb: assessing seed vs. safe-site limitation. _Ecology_ 91:1317-1328.

16.	Bruna, E. M. 2010. Journals can advance tropical biology and conservation by requiring data archiving.  *Biotropica* 42(4): 399–401.

49. Bruna, EM, IJ Fiske, and MD Trager. 2009. Habitat fragmentation and plant populations: Is what we know demographically irrelevant? _Journal of Vegetation Science_ 20:569-576.   

50. Callis, KL, LR Christ, J Resasco, DW Armitage, JD Ash, TT Caughlin, SF Clemmensen, SM Copeland, TJ Fullman, RL Lynch, C Olson, RA Pruner, EHM Vieira-Neto, R West-Singh, and EM Bruna. 2009. Improving Wikipedia: educational opportunity and professional responsibility. _Trends in Ecology & Evolution_ 24:177-179.    

51. Cardoso, E, MIB Cruzeiro Moreno, E. M., and HL Vasconcelos. 2009. Mudanças fitofisionômicas no Cerrado: 18 anos de sucesão ecológica na Estação Ecológica do Panga, Uberlândia, MG. _Caminhos de Geografia_ 10:254-268.    

52. Côrtes, M, V Gowda, WJ Kress, EM Bruna, and M Uriarte. 2009. Characterization of 10 microsatellite markers for the understory Amazonian herb _Heliconia acuminata_. _Molecular Ecology Resources _ 9 1261-1264.  [Ph. D. Thesis Chapter].  

53. Dattilo, W, TJ Izzo, BD Inouye, HL Vasconcelos, and EM Bruna. 2009. Recognition of host plant volatiles by _Pheidole minutula_ Mayr (Myrmicinae), an Amazonian ant-plant specialist. _Biotropica_ 41:642-646.   

54. Izzo, TJ, EM Bruna, HL Vasconcelos, and BD Inouye. 2009. Cooperative colony founding alters the outcome of interspecific competition between Amazonian plant-ants. _Insectes Sociaux_ 56:341-345.  

55. Kainer, KA, ML DiGiano, AE Duchelle, LHO Wadt, E Bruna, and JL Dain. 2009. Partnering for greater success: Local stakeholders and research in tropical biology and conservation. _Biotropica_ 41:555-562.  

56. Vasconcelos, HL, R Pacheco, RC Silva, PB Vasconcelos, CT Lopes, AN Costa, and EM Bruna. 2009. Dynamics of the leaf-litter arthropod fauna following fire in a Neotropical woodland savanna. _PLoS ONE_ 4:e7762.  

57. Bruna, EM, MR Darrigo, AM Furuya Pacheco, and HL Vasconcelos. 2008. Interspecific variation in the defensive responses of ant mutualists to plant volatiles. _Biological Journal of the Linnean Society_ 94:241-249.  

58. Costa, AN, HL Vasconcelos, EHM Vieira-Neto, and EM Bruna. 2008. Do herbivores exert top-down effects in Neotropical savannas? Estimates of biomass consumption by leaf-cutter ants. _Journal of Vegetation Science_ 19:849-854. [Ph. D. Thesis Chapter].  

59. Fiske, IJ, EM Bruna, and BM Bolker. 2008. Effects of sample size on estimates of population growth rates calculated with matrix models. _PLoS ONE_ 3:e3080.  [Ph. D. Thesis Chapter].  

60. Morris, WF, CA Pfister, S Tuljapurkar, CV Haridas, CL Boggs, MS Boyce, EM Bruna, DR Church, T Coulson, DF Doak, S Forsyth, J-M Gaillard, CC Horvitz, S Kalisz, BE Kendall, TM Knight, CT Lee, and ES Menges. 2008. Longevity can buffer plant and animal populations against changing climatic variability. _Ecology_ 89:19-25.    

61. Stocks, G, L Seales, F Paniagua, E Maehr, and EM Bruna. 2008. The geographical and institutional distribution of ecological research in the tropics. _Biotropica_ 40:397-404.  

65.	Vasconcelos, H. L., A. N. Costa, E. H. M. Vieira-Neto, and E. M. Bruna.  2008.  Efeitos da herbivoria por formigas  do gênero Atta Fabricius, 1804 (Hymenoptera: Formicidae) sobre a vegetação do Cerrado. Pp. 301-311 In: Insetos Sociais: da biologia a aplicação. Vilela, E.F.; Santos, I.A.; Schoereder, J.H.; Lino Neto, J.; Campos, L.A.O. & Serrão, J.E. (Eds.).  Editora da Univ. Federal de Viçosa. Viçosa, MG.  

62. Girao, LC, AV Lopes, M Tabarelli, and EM Bruna. 2007. Changes in tree reproductive traits reduce functional diversity in a fragmented Atlantic forest landscape. _PLoS ONE_ 2:e908.   

63. De Athayde, SF, GM Da Silva, J Kaiabi, M Kaiabi, HR De Souza, K Ono, and EM Bruna. 2006. Participatory research and management of Arumã (_Ischnosiphon gracilis_ Rudge Koern., Marantaceae) by the Kaiabi people in the Brazilian Amazon. _Journal of Ethnobiology_ 26:36-59. **[Cover article]**.  

64. Kainer, KA, M Schmink, H Covert, JR Stepp, EM Bruna, JL Dain, S Espinosa, and S Humphries. 2006. A graduate education framework for tropical conservation and development. _Conservation Biology_ 20:3-13.   

65. Trager, MD, and EM Bruna. 2006. Effects of plant age, experimental nutrient addition and ant occupancy on herbivory in a Neotropical myrmecophyte. _Journal of Ecology_ 94:1156-1163.  

66. Vasconcelos, HL, EHM Vieira-Neto, FM Mundim, and EM Bruna. 2006. Roads alter the colonization dynamics of a keystone herbivore in Neotropical savannas. _Biotropica_ 38:661-665. **[Recipient of the Julie S. Denslow Prize from the Association for Tropical Biology and Conservation]**.    

67. Bruna, EM, and MB Nogueira Ribeiro. 2005. Regeneration and population structure of _Heliconia acuminata_ in Amazonian secondary forests with contrasting land-use histories. _Journal of Tropical Ecology_ 21:127-131.  

68. Bruna, EM, and MK Oli. 2005. Demographic effects of habitat fragmentation on a tropical herb: Life-table response experiments. _Ecology_ 86:1816-1824.  

69. Bruna, EM, and MBN Ribeiro. 2005a. The compensatory responses of an understory herb to experimental damage are habitat-dependent. _American Journal of Botany_ 92:2101-2210.    

71. Bruna, EM, HL Vasconcelos, and S Heredia. 2005. The effect of habitat fragmentation on communities of mutualists: Amazonian ants and their host plants. _Biological Conservation_ 124:209-216.  

72. Doak, DF, WF Morris, C Pfister, BE Kendall, and EM Bruna. 2005. Correctly estimating how environmental stochasticity influences fitness and population growth. _American Naturalist_ 166:E14-E21.  **[Highlighted as a “Must Read” by the Faculty of 1000]**.  

73. Lapola, DM, EM Bruna, CG de Willink, and HL Vasconcelos. 2005. Ant-tended hemiptera in Amazonian myrmecophytes:  Patterns of abundance and implications for mutualism function. _Sociobiology_ 46:433-442.   

78.	Bruna E. M. & W. J. Kress.  2005.  Forest fragments and plant reproduction in Amazonian Brazil.  Pp. 141-146 in G. A. Krupnick & W. J. Kress, eds. Plant conservation: a natural history approach.  U. of Chicago Press.  

74. Bruna, EM, WJ Kress, F Marques, and OF da Silva. 2004. _Heliconia acuminata_ reproductive success is independent of local floral density. _Acta Amazonica_ 34:467-471. [Cover article].  

75. Bruna, EM, DM Lapola, and HL Vasconcelos. 2004. Interspecific variation in the defensive responses of obligate plant-ants: Experimental tests and consequences for herbivory. _Oecologia_ 138:558-565.  

76. Nakazono, EM, EM Bruna, and RCG Mesquita. 2004. Experimental harvesting of the non-timber forest product _Ischnosiphon polyphyllus_ in central Amazonia. _Forest Ecology and Management_ 190:219-225.  

80.	Lapola, D. M., E. M Bruna, and H. L. Vasconcelos.  2004.  Amizade tênue: relações mutualísticas entre plantas e formigas na Amazônia.  _Ciência Hoje_ 34(204): 28-33.  

83.	Bruna, E. M.  2004.  Biological impacts of deforestation and fragmentation.  Pages 85-90 in The Encyclopaedia of Forest Sciences.  J. Burley, J Evans, and J Youngquist, (eds.).  Elsevier Press, London.  

77. Bruna, EM. 2003. Are plant populations in fragmented habitats recruitment limited? Tests with an Amazonian herb. _Ecology_ 84:932-947.  

78. Lapola, DM, EM Bruna, and HL Vasconcelos. 2003. Contrasting responses to induction cues by ants inhabiting _Maieta guianensis_ (Melastomataceae). _Biotropica_ 35:295-300.    

79. Bruna, EM. 2002. Effects of forest fragmentation on _Heliconia acuminata_ seedling recruitment in central Amazonia. _Oecologia_ 132:235-243.  

80. Bruna, EM, and WJ Kress. 2002. Habitat fragmentation and the demographic structure of an Amazonian understory herb ( _Heliconia acuminata_). _Conservation Biology_ 16:1256-1266.  

81. Bruna, EM, O Nardy, SY Strauss, and SP Harrison. 2002. Experimental assessment of _Heliconia acuminata_ growth in a fragmented Amazonian landscape. _Journal of Ecology_ 90:639-649.  **_[Recipient of the John L. Harper Prize from the British Ecological Society]_**.  

82. Laurance, WF, TE Lovejoy, HL Vasconcelos, EM Bruna, RK Didham, PC Stouffer, C Gascon, RO Bierregaard Jr., SG Laurance, and E Sampaio. 2002. Ecosystem decay of Amazonian forest fragments, a 22 year investigation. _Conservation Biology_ 16:605-618.    

83. Hoeksema, JD, and EM Bruna. 2000. Pursuing the big questions about interspecific mutualism: A review of theoretical approaches. _Oecologia_ 125:321-330.  

84. Bruna, EM. 1999. Seed germination in rainforest fragments. _Nature_ 402:139.  

85. Harrison, S, and E Bruna. 1999. Habitat fragmentation and large-scale conservation: What do we know for sure? _Ecography_ 22:225-232.  

86. Bruna, EM, RN Fisher, and TJ Case. 1996. New evidence of habitat segregation between two cryptic species of Pacific skinks (_Emoia cyanura_ and _E. impar_). _Copeia_ 1996:998-1004.  

87. Bruna, EM, RN Fisher, and TJ Case. 1996. Morphological and genetic evolution appear decoupled in Pacific skinks (Squamata: Scincidae: _Emoia_). _Proceedings of the Royal Society of London Series B Biological Sciences_ 263:681-688. **[Cover article]**.  

88. Bruna, EM, RN Fisher, and TJ Case. 1995. Cryptic species of Pacific skinks (_Emoia_): Further support from mitochondrial DNA sequences. _Copeia_ 1995:981-983.  


### SOFTWARE (N=1)

1. Fournier, A., F. Stevens, M. Boone, and E. M. Bruna. 2020. refsplitr. author name disambiguation, author georeferencing, and mapping of coauthorship networks with Web of Science data. R package version 1.0.0. https://github.com/ropensci/refsplitr


### EDITORIALS, OUTREACH ARTICLES, & OTHER SCHOLARLY COMMUNICATION (N=14)

1.	Johnson-Ulrich, L. and E. Bruna. 2019. Emilio Bruna: Seed germination is lower in fragmented rainforest. Project Biodiversify [projectbiodiversify.org/emilio-bruna/](projectbiodiversify.org/emilio-bruna/)

2.	Bruna, E. M. 2019. _Biotropica_: the next 50 years. *Biotropica*.

3.	K. R. Zamudio, A. Kellner, C. Serejo, M. R. de Britto, C. B. Castro, P. A. Buckup, D. O. Pires, M. Couri, A. Brilhante Kury, I. Azevedo Cardoso, M. L. Monné, J. Pombal Jr., C. Mello Patiu, V. Padula, A. Dias Pimenta, R. Ventura, E.  Hajdu, J. Zanol, E. M. Bruna, J. Fitzpatrick, L. A. Rocha. 2018. Lack of support for Science and Education Fails Brazilian Society – Again. *Science.*.

4.	Bruna, Emilio M. 2017. Invasive new US visa rules hurt Americans too. *Americas Quarterly*. http://www.americasquarterly.org/content/academic-collaboration [Invited Essay].

5.	Harms, Kyle, J. Benitez-Malvido, & E. M. Bruna. 2017. 2016 Alwyn Gentry Awards and Luis F. Bacardi Award Recipients. *Biotropica* [Editorial].

6.	Bruna, E. M. 2016. Biotropica renames its "Outstanding Paper" awards for two pioneering scientists. *Biotropica* 48(6): 929 [Editorial].

10.	E. M. Bruna, M. Peña-Claros, Bryan Finega, and B. A. Kaplin. 2016. A New Data Archiving Policy for _Biotropica._ *Biotropica*, 48(2): 139-140. [Editorial].

11.	E. M. Bruna. 2014. Biotropica to become an ‘online-only’ journal in 2015. *Biotropica* 46(6): 782. [Editorial].

12.	E. M. Bruna. 2014. 2014 Alwyn Gentry Awards, Luis F. Bacardi Award, and ATBC Honorary Fellows. *Biotropica* 46(6): 779-781. [Editorial].

13.	E. M. Bruna. 2014. A word from the Editor-in-Chief. *Biotropica* 46(4): 377 [Editorial].

17.	Bruna, E. M. 2010.  Announcement: _Biotropica_ Award for Excellence in Tropical Biology and Conservation. *Biotropica* 42(4): 518–519 [Editorial].

18.	Bruna, E. M. and K. A. Kainer.  2005.  A delicate balance in Amazonia.  *Science* 307:1044-1045. [Response to published article].  

19.	Bruna, E. M.  2003.  "For the Love of Nature".  *Science's Next Wave* Online Magazine. [Invited essay].

20.	Bruna, E. M. 2002. A biologist’s guide to fragmenting the Amazon (including why it’s a bad idea).  *Conservation Biology*, 16(5): 1446-1448. [Book review].  

### PUBLICATIONS BY LAB MEMBERS (N = 16; see co-authorship philosophy above; lab member underlined).

1.	Costa, A. N. and Vieira-Neto, E. H. M. 2016. Species turnover regulates leaf-cutter ant densities in environmental gradients across the Brazilian Cerrado. *Journal of Applied Entomology* 140(2016):474-478. 

2.	M. Tabarelli, A. V. Neto, I. R. Leal, and A. V. Lopes (Eds.).  2014. Serra Grande: Uma Floresta de ideas.  Editora Universitária da UFPE. Recife. 672 pp.

3.	Cruz Neto O, Aguiar AV, Twyford AD, Neaves LE, Pennington RT, and Lopes AV. 2014. Genetic and ecological outcomes of _Inga vera_ subsp _affinis_ (Leguminosae) Tree plantations in a fragmented tropical landscape. *PLoS ONE* 96: e99903.

4.	Lucas CM, Schoengart J, Sheikh P, Wittmann F, Piedade MTF, and McGrath DG. 2014. Effects of land-use and hydroperiod on aboveground biomass and productivity of secondary Amazonian floodplain forests. *Forest Ecology and Management* 319:116-127. [Ph.D. thesis chapter].

5.	Soares SM, Machado IC, Aguiar AV, and Lopes AV. 2014. Dioecy in the Caatinga, a Brazilian tropical  dry forest: typical reproductive traits of a low frequent sexual system. *Plant Systematics and Evolution* 300:1299-1311.

6.	Tabarelli M, Aguiar AV, Robeiro MC, and Metzger JP. 2012. A conversão da Floresta Atlântica em paisagens antrópicas: lições para a conservação da diversidade biológica das florestas tropicais. *Interciencia* 37:88-92.

7.	Lucas CM, Mekdece F, Nascimento CMN, Holanda A-SS, Braga J, Dias S, Sousa S, Rosa PS, and Suemitsu C. 2012. Effects of short-term and prolonged saturation on seed germination of Amazonian floodplain forest species. *Aquatic Botany* 99:49-55. [Ph.D. thesis chapter].

8.	Horn, M., S.B. Correa, P. Parolin, B.J.A. Pollux, J.T. Anderson, C. Lucas, P. Widmann, A. Tiju, M. Galetti, and M. Goulding. 2011. Seed dispersal by fishes in tropical and temperate waters: the growing evidence.  *Acta Oecologia* 37:561-577.

9.	Tabarelli M, Aguiar AV, Ribeiro MC, Metzger JP, and Peres CA. 2010. Prospects for biodiversity conservation in the Atlantic Forest: lessons from aging human-modified landscapes. *Biological Conservation* 143:2328-2340.

10.	Gagnon, P.R., Passmore, H.A., Platt, W.J., Paine, C.E.T., Myers, J.A. and Harms, K.E. 2010. Does pyrogenicity protect burning plants? *Ecology* 91: 3481-3486 [Cover Article]. 

11.	Trager, M. D., S. Bhotika, J. A. Hostetler, G. V. Andrade, M. A. Rodriguez-Cabal, C. S. McKeon, C. W. Osenberg, and B. M. Bolker. 2010. Benefits for plants in ant-plant protective mutualisms: A meta-analysis. *PLoS ONE* 5:e14308.

12.	Parolin P, C. Lucas, M.T.F. Piedade, & F. Wittmann. 2010. Drought responses of flood-tolerant trees in Amazonian Floodplains. *Annals of Botany* 105(1):129-39. [Invited article]

13.	Aguiar AV, and Tabarelli M. 2010. Edge effects and seedling bank depletion: the role played by the early successional palm _Attalea oleifera_ (Arecaceae) in the Atlantic Forest. *Biotropica* 42:158-166.

14.	Duchelle, A.E., K. Biedenweg, C. Lucas, J. Radachowsky, D. Wojcik, M. Londres, D. Alvira, W. Bartels, A. Virapongse, and K.A. Kainer. 2009. Graduate students and knowledge exchange with local stakeholders: Possibilities and preparation.  *Biotropica* 41(5): 578-585.

15.	Lucas, C.M. 2008. Within flood season variation in fruit consumption and seed dispersal by two characin fishes of the Amazon. *Biotropica* 40(5): 581–589.

16.	Hartter, J., C. Lucas, A. Gaughan, and L.L. Aranda. 2008. Detecting tropical dry forest succession in a shifting cultivation mosaic of the Yucatán Peninsula, Mexico.  *Applied Geography* 28: 134-149.


### PUBLICLY ARCHIVED DATASETS & CODE (N=21)

1. Emilio M. Bruna, Audrey C. Smith, Leandra Merz, Jesse Borden, Chris K. Gulick, & Akhil R. Kshirsagar. (2021). Data and Code from: Assessing the effect of article processing charges on the geographic diversity of authors using Elsevier's 'Mirror Journal' system. (v1.0.0). Zenodo. https://doi.org/10.5281/zenodo.5500293

2. Costa et al. (2018) Data from: The relative influence of an environmental gradient and an ecosystem engineer on seedling communities in a Neotropical savanna. Dryad Digital Repository https://doi:10.5061/dryad.vf1gq0q 

2.	Emilio M. Bruna. (2018, September 13). embruna/Costa-etal-PeerJ-2018: First release of code used in Costa et al 2018 PeerJ (Version v1.0.0). Peerj. Zenodo. http://doi.org/10.5281/zenodo.1418482 

3.	Espin, J., et al. (2017) Data from: A persistent lack of international representation on editorial boards in environmental biology. Dryad Digital Repository. https://doi.org/10.5061/dryad.mh189

4.	Bruna, E. M. 2017. Code (v1.0) used in “A persistent lack of international representation on editorial boards in environmental biology, Espin et al.”  Zenodo http://doi.org/10.5281/zenodo.1067800

5.	Vieira-Neto EHM, Vasconcelos HL, Bruna EM (2016) Data from: Roads increase population growth rates of a native leaf-cutter ant in Neotropical savannahs. Journal of Applied Ecology https://doi.org/10.5061/dryad.1s4f2

6.	Costa AN, Vasconcelos HL, Bruna EM (2016) Data from: Biotic-drivers of seedling establishment in Neotropical savannas: selective granivory and seedling herbivory by leaf-cutter ants as an ecological filter. Journal of Ecology https://doi.org/10.5061/dryad.1hj56

7.	Mundim FM, Bruna EM (2016) Data from: Is there a temperate bias in our understanding of how climate change will alter plant-herbivore interactions? A meta-analysis of experimental studies. The American Naturalist https://doi.org/10.5061/dryad.dn048

8.	Bruna EM, Izzo TJ, Inouye BD, Vasconcelos HL (2014) Data from: Effect of mutualist partner identity on plant demography. Ecology https://doi.org/10.5061/dryad.5kc45

9.	Bruna E.M. 2014. Code (v1.0) used in "Effect of mutualist partner identity on plant demography. Ecology”. Zenodo: doi:10.5281/zenodo.11650. Available for improvement at https://github.com/embruna/ant-plant-demography. 

10.	Cho AH, Johnson SA, Schuman CE, Adler JM, Gonzalez O, Graves SJ, Huebner JR, Marchant DB, Rifai SW, Skinner I, Bruna EM (2014) Data from: Women are underrepresented on the editorial boards of journals in environmental biology and natural resource management. PeerJ https://doi.org/10.5061/dryad.6jn86.2

11.	Cho et al. 2014. Code used in “Women are underrepresented on the editorial boards of journals in environmental biology and natural resource management. PeerJ”:: https://github.com/embruna/Editorial-Board-Gender 

12.	Corrêa Côrtes M. et al. 2013. Low plant density enhances gene dispersal in the Amazonian understory herb Heliconia acuminata. Molecular Ecology Dryad Digital Repository: doi:10.5061/dryad.b003f

13.	Passmore, H. A et al. 2012. Data from: Resilient networks of ant-plant mutualists in Amazonian forest fragments. PLoS ONE. doi:10.5061/dryad.pf2r 

14.	Copeland, S. M. et al. 2012. Data from: Effects of experimentally elevated precipitation and nitrogen on soil fertility and plant growth in a Neotropical savanna. Ecosphere. Dryad Digital Repository: doi: 10.5061/dryad.dg380p9q

15.	Bruna EM, et al. 2011. Data from: Asymmetric dispersal and colonization success of Amazonian plant-ants queens. PLoS ONE. Dryad Digital Repository. doi:10.5061/dryad.h6t7g

16.	Bruna, E. M. and A. Segalin de Andrade. 2011. Data from: Phenotypic plasticity in plant responses to edge effects: experimental test with an Amazonian understory herb. American Journal of Botany. Dryad Digital Repository: doi:10.5061/dryad.553hc134

17.	Microsatellite sequences from Cortes, MC et al. 2009. Characterization of 10 microsatellite markers for the understorey Amazonian herb Heliconia acuminata. Molecular Ecology Resources. Genbank.

18.	Stocks G. et al. 2008. Data from: The geographical and institutional distribution of ecological research in the tropics. Biotropica. Dryad Digital Repository: doi:10.5061/dryad.9097 

19.	Sequences used in Mitochondrial DNA sequences from Bruna, E. M. et al. 1996.  Morphological and genetic evolution appear decoupled in Pacific skinks (Emoia). Proc. Roy. Soc. Lond. B: Genbank.

20.	Heliconia acuminata Demographic Data. Seed set: http://dx.doi.org/10.6084/m9.figshare.1273926 Leaf Length vs. Area: http://dx.doi.org/10.6084/m9.figshare.92691


### MANUSCRIPTS IN PREPARATION (N=10, drafts available upon request). 
	
1.	E. S. Parsons and E. M. Bruna. Assessing the magnitude of abiotic edge effects in fragmented landscapes: revisiting the paradigm with data. In preparation for *Biological Conservation* [MA Thesis chapter].

2.	E. M. Bruna, M. Uriarte, and W. J. Kress. Abundance and demography of the understory herb *Heliconia acuminata* (Heliconiaceae) in an experimentally fragmented landscape in the Central Amazon (1997-2009). In preparation for *Ecology*.


3. Russell, A.E., T.M. Aide, E. Braker, E. M. Bruna, C. N. Ganong, R. D. Hardin, K. D. Holl, S. C. Hotchkiss, J. Klemens, E. K. Kuprewicz, L. G. Lohmann, S. K. Macey, G. Middendorf, C. R. Nufio, R. 
Ostertag, J. S. Powers, S. Russo, J. L. Stynoski, C. G. Wills, U. Valdez. Novel approaches to bringing tropical biology into the undergraduate classroom: the OCELOTS Network. In preparation for *Biotropica*.

3.	E. H. M. Vieira-Neto, F. M. Mundim, and E. M. Bruna. Closed and open demographic models give contrasting patterns of inter-ppopulation dynamics in a long-lived superorganism. In preparation for *Ecology.*

4.	Goring, S., K.S. Whitney, E. M. Bruna, A. L. Jacob, and T. Poisot. Ten Simple Rules to Make Scientific Content More Accessible. Preprint at: DOI: [10.22541/au.150844289.92609826](https://doi.org/10.22541/au.150844289.92609826)

5.	Tolentino,M., M. Anciães, E. M. Bruna, and M. Uriarte. *In revision*. Local and landscape factors mediate reproductive success of Heliconia acuminata in a fragmented landscape. *Landscape Ecology*. 

6.	Corrêa Côrtes, M., M. Uriarte, W. J. Kress, J. B. Illian, and E. M. Bruna. *In revision*. Why are the spatial distribution of individual plants and genotypes decoupled? A framework to assess the contribution of ecological interactions and environmental filtering. *Ecology Letters* [Ph.D. Thesis Chapter].

4.	Bruna, E. M. and W. Hahn.  In preparation. Is Latin American ecology really on the rise? Cross-national patterns of productivity and collaboration by Latin American scientists. In preparation for PLoS Biology.

5.	Rubim, P., D. M. S. Matos, M. Uriarte, and E. M. Bruna. Local density influences the growth of seedlings of an Amazonian understory herb. In preparation for *Biotropica* [Ph.D. Thesis Chapter].

6.	Loiselle, B. A., E. M. Bruna, R. Buschbacher, and S. Athayde. In prep. How can Brazilian Studies and partnerships with Brazilian institutions shape the perception of tropical conservation and development issues at US universities? Lessons from the University of Florida. Brazilian Studies in the United States: The road ahead. Yale University, FGV, and The Ministry of Education in Brazil.

7.	Rubim, P. R., M. Uriarte, O. Ferreira, and E. M. Bruna. Neighborhood effects and the reproductive effort of a tropical perennial herb. In preparation for *Ecology* [Ph.D. Thesis Chapter].

9.	Ferreira, A. M. A. P. Faria, H. L. Vasconcelos, E. M. Bruna, A. S. Franco Pinheiro Moreira. Effect of nitrogen deposition on metabolism, biomass increase and species richness in a grass community of the Brazilian Cerrado.  In preparation for *Plant & Soil*.

10.	Hyde, J. L., Bohlman, S. A., Athayde, S., Bruna, E. M., Valle, D.R. In prep. A lack of open data standards for large infrastructure project hampers social-ecological research in the Brazilian Amazon. In preparation for *Environmental Science and Policy*. 


### WEB PAGES AND OTHER FORMS OF DIGITAL COMMUNICATION

1. Over 30 Wikipedia pages edited with students as part of graduate and undergraduate courses in Plant Animal Interactions and Tropical Ecology. Complete at: http://en.wikipedia.org/wiki/User:Embruna 

2. Biotropica.org: The Editor’s Blog. A forum for sharing information about the journal Biotropica, its ongoing initiatives, announcements debates on recent publications, and advice for authors. >80,000 views since launched in August 2013, http://biotropica.org/ 

3. BrunaLab.org / “Between the 23s” (lab web page and blog): In addition to hosting publications, data, and other information on current lab activities, we provide resources for the broader community on topics (e.g., resources for beginners on making figures in R or version control with GitHub).  We also maintain a compendium on smartphone applications for fieldwork, which is responsible for most of the sites 113,000 page views since January 2013. http://brunalab.org/ 

4. “Jean Theodore Descourtilz (1796-1855) and the Ornithologie Bresilienne.” A website created by TCD graduate students in my Tropical Ecology class to provide background information and an analysis of artwork acquired by the Harn Museum of Art on their behalf.  https://descourtilz.wordpress.com/ 


### COURSE DEVELOPMENT TEACHING EXPERIENCE

\begingroup 
\setlength{\leftskip}{.2cm}  


__Courses Taught at the University of Florida__  
Ecology and Conservation of Tropical Wildlife (Undergraduate, 03,05,07,11,12,14,18)  
Data Collection & Management for Latin American Studies (Graduate, 2019)  
Plant-Animal Interactions (Graduate, 2004, 2006, 2008, 2010)  
Fundraising for Tropical Conservation & Development (Graduate, 2013, 2016, 2018, 2020)  
Scientific Publishing (Graduate, 2014, 2015, 2017, 2018)  
Ecological Principles for Development & Conservation Professionals (Graduate, 2010, 2011, 2012)  
Tropical Forest Community Ecology (Graduate, 2000)  
Design and Methods of Research in Latin American Studies (Graduate, 2008, 2010)  
Research Methods in Tropical Conservation & Development (Graduate, 2003-2007)  
Seminar in Wildlife Ecology and Conservation (Graduate, 2003, 2004)  
Social Media Workshop (Graduate, 2016)  

\endgroup 

\begingroup 
\setlength{\leftskip}{.2cm}  

__Other Teaching Experience__  


*__Guest Lectures in UF Courses__*  
Diverse Perspectives in Conservation(WIS4934, 2021)
Human Footprint on the Landscape (GEO3352, 2019)  
Facets of Sustainability (IDS2154, 2011, 2013)  
Environmental Planning & Design (EES 6051, 2016,2018)  
The Amazon (LAS6290, 2009, 2011)  
Design & Methods of Research in Latin American Studies (Graduate, 2019, 2020)  
Discovering Research & Communicating Science (IDH3931, 2015)  
Wildlife Techniques (WIS4945C, 2005)  
Development Theory & Practice (LAS6938, 2010)  
Wildlife Population Modeling (WIS6466, 2003, 2006, 2008, 2010)  
Principles of Wildlife Ecology & Conservation (WIS6934, 2008)  
Luso-Brazilian Civilization (POW3500, 2004)  

*__Courses Taught & Guest lectures at Other Institutions__*  
Univ. Federal de Uberlândia: Mechanisms of Species Coexistence (Graduate Course, 2006)  
Univ. Federal de Uberlândia: Data Management & Archiving (Graduate Course, 2012, 2014)  
Univ. Federal de Uberlândia: Scientific Publishing (Graduate Course, 2011)  
INPA: Population Ecology (Guest Lecturer 2002, 2003)  
INPA: Community Ecology (Guest Lecturer 2002)

*__Participation in Field Courses__*  
OTS 3M Field Course (2001)  
OTS Amazonian Ecosystems Field Course (2001)  
Antioch College Semester Abroad in Brazil (1999, 2001)  
Univ. Federal do Amazonas, Fragmented Landscapes Field Course (2000, 2002)  

\endgroup 

### GRADUATE STUDENTS ADVISED
```{r GradStudentsA, echo=FALSE,message = FALSE,warning=FALSE}
# library(flextable)
# https://cran.r-project.org/web/packages/flextable/vignettes/format.html#borders
# df <- grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="advisor") %>% select(-role)
# table1<-df %>% regulartable() %>% autofit() %>% 
# width(j=~Degree,width=.3) %>% width(j=~Year,width=.9) %>% width(j=~Instititution,width=.1)
# table1 <- fontsize(table1, part = "header", size = 11) 
# table1 <- border_remove(x = table1)
# table1
```


```{r GradStudents, echo=FALSE,message = FALSE,warning=FALSE}

grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="advisor") %>% select(-role)
kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
    col.names = NULL,
    longtable = T,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)

```

Students under my supervision have been awarded over $35,000 in grants to support their research and been the recipients of prestigious fellowships and awards to support their studies: 

*	FLAS Fellowship (S. Parsons)
*	NSF Predoctoral Fellowships (M. Trager, S. Copeland)
*	UF IGERT Fellowship (C. Lucas)
*	Inter-American Foundation Grassroots Development Fellowship (C. Lucas)
*	UF Alumni Fellowship (M. Trager)
*	Fulbright Fellowship (A. Neto)
*	Science Without Borders Doctoral Fellowship (E. V. Neto, F. Mundim).
*	NSF Doctoral Dissertation Enhancement Grant (C. Lucas)
*	UF-WEC Jennings Scholarship (A. Neto, M. Trager, F. Mundim, G. Iacona) 
*	UF-CALS Doris Lowe & Earl & Verna Lowe Scholarship (C. Lucas, E. V. Neto). 

Research by my students has also been recognized for its excellence: 

*	Fabiane Mundim: 2016 UF-WEC High-Impact Publication
*	Ana Cecilia Silva: Honorable Mention, 2015 Charles Wood Thesis Award, UF Latin American Studies
*	Fabiane Mundim: Honorable Mention, 2012 OTS Outstanding Paper Competition 
*	Christine Lucas: 2012 Marianne Schmink Award for the University of Florida’s outstanding Dissertation in Tropical Conservation and Development.
*	Ernane Vieira Neto: 2011 E. Lucy Braun Award (Outstanding poster presented at the Annual Meeting of the Ecological Society of America).
*	Shannon Moore, a high school student in my lab as part of UF’s Student Science Training Program (SSTP), was awarded the prize for the best oral presentation at the 2010 SSTP Symposium.
*	Matthew Trager: 2005 Wildlife Grad Student Assoc. Outstanding Research Award (MS Category).


### DOCTORAL STUDENT COMMITTEE SERVICE, UNIVERSITY OF FLORIDA

```{r DocCmte, echo=FALSE,message = FALSE,warning=FALSE}
grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="doc_cmte") %>% select(-role)

kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
                  col.names = NULL,
                  row.names = FALSE,
                  booktabs=T,
                  longtable = T, 
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)

```
<!-- **Wildlife Ecology & Conservation**: David Mason (in progress), Flavia Montaño Centellas (2018), Margo Stoddard (2017), Rajeev Pillay (2016), Rosalyn Johnson (2016), Gonzalo Rivas (2015), Oscar Gonzalez (2015), Dan Thornton (2010), Ivan Diaz (2008), Christa Zweig (2008), Traci Darnell (2006)  **Forest Resources & Conservation**: Andrea Irons (in progress), Demian Gomez Damiano (2020), Jacy Hyde (2019), Christie Klimas (2010)  **Biology (*formerly Depts. of Botany & Zoology*)**: Maria Beatriz Cortez (in progress), Johanna R. Jantzen (2020), Trevor Caughlin (2013), Kristine Callis (2013), Mollie Brooks (2012), Silvia Alvarez-Clare (2012), C. Seabird McKeon (2010), Joseph Veldman (2010), Jennifer Schafer (2010), Alex Jahn (2009), Silvia Lomáscolo (2008), Bonifacio Mostacedo (2007)  **Interdisciplinary Ecology**: Joanna Tucker (2010), Matt Trager	(2009)  **Entomology**: Jade Badon (2018), Pablo Allen (2017), David Serrano (2006)  **Anthropology**: Scott Macrae (2017)  **Columbia University**: Marina Cortes (Ecology, Evolution, Behavior (2012) -->



### MASTER’S STUDENT COMMITTEE SERVICE
```{r MastersCmte, echo=FALSE,message = FALSE,warning=FALSE}

grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="masters_cmte") %>% select(-role)
kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
        longtable = T, 
    col.names = NULL,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)

```
<!-- **Wildlife Ecology & Conservation**: Lauren Trotta (2016), Brittany Bankovich (2014), Nathan Marcy (2010), Kristen Aaltonen (2009), Mariano Rodriguez Cabal (2007)  **Forest Resources & Conservation**: Jennifer Holm (2007), Christie Klimas (2006)  **Biology (*formerly Depts. of Botany & Zoology*)**: Tania Kim (2006), Silvia Alvarez Clare (2004)  **Interdisciplinary Ecology**: Jamie Cotta (2006)  **Entomology**: Teresa Cooper (2006)  **Latin American Studies**: Crisne Lebron (2015), Carly Voight (2010), Laura Fonseca (2009), Jennifer Davies (2003), **Anthropology**: Autumn Rose (in progress). -->
		
### MEMBER OF PROPOSAL REVIEW, THESIS REVIEW, OR THESIS DEFENSE COMMITTEE
```{r external, echo=FALSE,message = FALSE,warning=FALSE}

other<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="other") %>% select(-role,-Program)
kbl(other,digits = 1,
                  format = "latex",
                  align="l",
        longtable = T, 
    col.names = NULL,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)

```




### POSTDOCTORAL, SABBATICAL, & POSTGRADUATE SCHOLARS 
```{r lab_members, echo=FALSE,message = FALSE,warning=FALSE}
lab_members<-read_csv("./cv_files/lab_members.csv") 
lab_members$cat<-as.factor(lab_members$cat)
lab_members$cat <- ordered(lab_members$cat, levels = c("postdoc","sab" ,"postgrad", "vis_grad","ug","hs"))
lab_members2<-lab_members %>% 
  filter(cat=="postdoc"|cat=="sab"|cat=="postgrad") %>% 
  arrange(order(cat)) %>% 
  select(-cat) %>% 
  replace_na(list(Name=" ", Institution=" ", Position=" ", Year=" "))

kbl(lab_members2,digits = 1,
    format = "latex",
    align="l",
    longtable = T, 
    col.names = NULL,
    row.names = FALSE,
    booktabs=T,
    linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
      
```

<!-- **Doctoral Defense Committee:** Helen Belan (U. Federal de Uberlândia, Brazil, 2020), Alan Nilo da Costa (U. Federal de Uberlândia, Brazil, 2013). **Doctoral Dissertation Examiner:** Talita Reis (UNICAMP, Brazil, 2015), Mauricio Bonesso Sampaio (UNICAMP, Brazil, 2012), Maria Rosa Darrigo (UNICAMP, Brazil, 2011), Sjirk Geerts (Stellenbosch University, South Africa, 2011), Rafael Soares de Arruda (INPA, Brazil, 2008), Thiago Junqueira Izzo (INPA, Brazil, 2005). **Doctoral Proposal Defense**: Laura Vivian Barbosa (U. Federal de Uberlândia, Brazil, 2014) **Master's Thesis Defense Committee**: Jonas B. Marvalhas (U. Federal de Uberlândia, Brazil 2013), Ernane Vieira Neto (U. Federal de Uberlândia, Brazil, 2008), Alan Nilo da Costa (U. Federal de Uberlândia, Brazil, 2007), Daniel Mascia Vieira (Universidade de Brasília, Brazil, 2002) -->

<!-- Carine Emer			INPA, Brazil				M.S. Thesis Examiner, 2011 -->
<!-- Flávio de Oliveira Rodrigues	INPA, Brazil				M.S. Thesis Examiner, 2011 -->
<!-- Waldete Castro Lourenço		INPA, Brazil				M.S. Thesis Examiner, 2009 -->
<!-- Simone B. Fontoura		INPA, Brazil				M.S. Thesis Examiner, 2007 -->
<!-- Paula M. Pedrosa			INPA, Brazil				M.S. Thesis Examiner, 2004 -->

<!-- Carine Emer 			INPA, Brazil				M.S. Proposal Examiner, 2009 -->
<!-- Simone Benedet Founatura	INPA, Brazil				M.S. Proposal Examiner, 2006 -->
<!-- Thiago Junqueira Izzo		INPA, Brazil				M.S. Proposal Examiner, 2002 -->

<!-- Melina Alcalá			UFSCar, Brazil				M.S. Qualifying Exam, 2009 -->
<!-- Raquel Negrão Baldoni		UFSCar, Brazil				M.S. Qualifying Exam, 2009 -->

<!-- Pedro B. Vasconcelos		U. Federal de Uberlândia, Brazil		B.S. Thesis Defense, 2009 -->
<!-- Fabiane M. Mundim 		U. Federal de Uberlândia, Brazil		B.S. Thesis Defense, 2007 -->

### UNDERGRADUATE THESIS STUDENTS, HIGH SCHOOL RESEARCHERS, & VISITING GRADUATE STUDENTS  
```{r lab_members2, echo=FALSE,message = FALSE,warning=FALSE}
lab_members<-read_csv("./cv_files/lab_members.csv") 
lab_members$cat<-as.factor(lab_members$cat)
lab_members$cat <- ordered(lab_members$cat, levels = c("postdoc","sab" ,"postgrad", "vis_grad","ug","hs"))
lab_members3<-lab_members %>% 
  filter(cat=="ug"|cat=="hs"|cat=="vis_grad") %>% 
  arrange(order(cat)) %>% 
  select(-cat) %>% 
  replace_na(list(Name=" ", Institution=" ", Position=" ", Year=" "))

kbl(lab_members3,digits = 1,
                  format = "latex",
                  align="l",
        longtable = T, 
    col.names = NULL,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)

```

\begingroup 
\setlength{\leftskip}{.2cm}

*__Research Interns:__* _2007_: Wesley Dáttilo da Cruz, Univ. Estadual do Norte Fluminense (Brazil), Jefferson José Valsko da Silva, Universidade do Norte Fluminense (Brazil). _2005-2007_: Renata Pacheco do Nacimento and Cauê Thomé Lopes, Univ. Federal de Uberlândia (Brazil). _2005-2006_: Polyanna Custodio Duarte, Univ. Federal de Uberlândia (Brazil). _2006_: Waldete Castro Lourenço, Univ. Federal do Amazonas (Brazil), Elisabete Marques da Costa, Univ. Federal de Pernambuco (Brazil). _2005_: Bruno Turbiani, Universidade Estadual Paulista (Brazil). _2004_: Cristina Escate, Universidade Federal do Amazonas (Brazil), Simone Benedet, Universidade do Vale do Rio do Sinos (Brazil). _2003_: Cris Follman Jurinitz, Univ. Federal do Rio Grande do Sul (Brazil), Denise Cruz, Univ. Federal do Rio de Janeiro (Brazil). _2003-2004_: David M. Lapola, Universidade Estadual Paulista (Brazil). _2002_: Maria Beatriz Nogueira, Universidade de São Paulo (Brazil). _2001-2002_: Sylvia Heredia, Universidad de los Andes (Colombia). _2001_: Obed Garcia, INPA (Brazil), Olavo Nardy, UNESP (Brazil).

\endgroup

### SERVICE - UNIVERSITY OF FLORIDA  

\begingroup 
\setlength{\leftskip}{.2cm}
Samuel P. Harn Museum of Art Faculty Council (2012-2015)  
Selection Committee, UF International Educator of the Year Award (2006)  
Selection Committee, UF Teacher/Scholar of the Year (2015)  
UF Research Foundation Professorship Selection Committee (2010)  
Fulbright Fellows Campus Interview Committee  (2019)  
Catalyst Fellow, UF Innovation Academy Catalyst Challenge (2018)  
External Advisory Committee, Institute of Museum & Library Services Grant (2015-2018)  
International Outreach Advisory Council, Graduate School (2014-Present)  
Internal Advisory Board, Innovation through Institutional Integration (I3) program (2010-2014)  
Administrative Council, QSE3 IGERT (2008-2014)  
Peer Teaching Evaluation for Dr. Michelle Mack, UFL Department of Botany (2006)    

\endgroup 

### SERVICE - UF COLLEGE OF AGRICULTURAL AND LIFE SCIENCES  
\begingroup 
\setlength{\leftskip}{.2cm}

IFAS International Programs Advisory Team (2020-Present)  
UF-CALS Outstanding Thesis Selection Committee (2020)  
York Distinguished Lecture Selection Committee (2015)  
Search and Screen Committee, CALS Quantitative Sciences Faculty Positions (2013)  
Coordinating Committee, School for Natural Resources & the Environment (2012)  
Invited Speaker, College of Agricultural & Life Sciences Teaching Grantsmanship Workshop (2012)  
Mentorship Committee for Dr. Luke Flory, Dept. of Agronomy (2012)  
IFAS Faculty Professional Development Advisory Committee (2012-2013)  
Selection Committee, College of Agricultural & Life Sciences Teaching and Advising Awards (2012)  
Invited Speaker, College of Agriculture and Life Sciences Teaching Enhancement Symposium (2010)  
College of Agricultural & Life Sciences Undergraduate Scholarships & Awards Committee (2007-2009)  
Unifas Focus Group (Teaching Section), College of Agriculture and Life Sciences (2007)  
Unifas Advisory Committee, College of Agriculture and Life Sciences (2006-2007)  
Invited Speaker, College of Agriculture and Life Sciences Teaching Enhancement Symposium (2005)  
Commencement Marshal, College of Agricultural and Life Sciences (2004, 2014,2015, 2018)   
SNRE Seed Grant and New Faculty Support Grant Programs (2005)  

\endgroup 

### SERVICE - UF DEPARTMENT OF WILDLIFE ECOLOGY & CONSERVATION  

\begingroup 
\setlength{\leftskip}{.2cm}

Research Committee (2005-2007, 2020-present)  
Space Committee (2019)  
Communications Committee (2014-Present)  
Graduate Program Committee (2005-2012)  
International Programs Committee (2006-2010)  
Steering Committee, PSTC Compton Fellowship Program (2002-2010)  
Seminar Series Coordinator (2003-2004)  
Seminar Series Coordinator (2015)  
Chair, Pre-Tenure Mentorship Committee for Dr. Robert Fletcher (2009-2012)  
Search and Screen Committee, Research Asst. Professor, Zoo Wildlife Conservation Biology (2020)   
Search and Screen Committee, Asst. Professor of Population Ecology (2017)  
Search and Screen Committee, Department Head (2006)  
Search and Screen Committee, Asst. Professor of Landscape Ecology (2004)  
Search and Screen Committee, Asst. Professor of Conservation Genetics, WEC (2004)  
Chair, Peer Teaching Evaluation Committee for Dr. Ethan White (2019-2020)  
Chair, Peer Teaching Evaluation Committee for Dr. Morgan Ernest (2017-2018)  
Chair, Peer Teaching Evaluation Committee for Dr. Lyn Branch (2011)  
Chair, Peer Teaching Evaluation Committee for Dr. Bill Pine (2010)  
Chair, Peer Teaching Evaluation Committee for Dr. Robert Fletcher (2009)  
Tenure Mentorship Committee for Dr. Nia Morales (2021-2022) 
Peer Teaching Evaluation Committee for Dr. Madan Oli (2003)  
Peer Teaching Evaluation Committee for Dr. Bill Pine (2015)  

\endgroup 

### SERVICE - UF CENTER FOR LATIN AMERICAN STUDIES  
\begingroup 
\setlength{\leftskip}{.2cm}

LAS Faculty Advisory Council (2020-2023)  
LAS Bylaws Revision Committee (2020-2021)  
LAS Merit Evaluation Committee (2015-2017)  
LAS Graduate Admissions and Fellowship Committee (2007)  
Chair, Search and Screen Committee, Lecturer in Latin American Studies (2015)  
Chair, LAS Awards and Scholarship Committee (2019)  
Search and Screen Committee, LAS Communications Coordinator (2015)  
Bacardi Seminar Series Coordinator (Spring 2015)  
Academic Advisor, Tropical Conservation and Development (TCD) Program (2008-2011) 
Faculty Advisor, TCD Graduate Student Organization (2008-2016)  
Steering Committee, TCD Program (2002-2008, 2010-2016, 2018-present)  
Chair, TCD Fellowship Committee (2012)  
Chair, TCD Field Research Grants Committee (2004, 2008, 2009, 2010, 2015, 2020)  
Chair, Marianne Schmink Award Selection Committee (2010, 2011, 2013)  
TCD Field Research Grants Committee (2003, 2004)  
TCD Fellowship Committee (2003-2005)  
Organizing Committee, TCD Strategic Planning (2007-2008)  
Curriculum Committee, Master’s Program in Sustainable Development Practice (2010-2012)  
Advisory Council, Amazon Conservation Leadership Initiative (2004-2005)  
Advisory Committee, Pan-Amazon Community of Practice Project (2018-2020) 

\endgroup  

### SERVICE - OTHER INSTITUTIONS  
\begingroup 
\setlength{\leftskip}{.2cm}

Tenure and Promotion Portfolio Evaluations: 2021 (2), 2020 (3), 2018 (2), 2017 (1), 2016 (3), 2015 (1), 2011 (1)  
ASN/SSE/SSB Committee on Development a Professional Code of Ethics (2018-2019)  
External Advisor, 2nd Planning Workshop, Brazilian Biodiversity and Ecosystem Services Synthesis Center (2018)  
Discussant, Research & Writing Conference, Florida Education Fund/McKnight Doctoral Fellowship Program (2016)  
Co-host & Co-organizer, UC Davis Population Biology Workshop in Ecology (2000)  
Student Representative, UC Davis Population Biology GRT Executive Committee (1996-1997)  
UC San Diego EAP Selection Committee, Tropical Biology Program (1994)  

\endgroup 

### SERVICE - ASSOCIATION FOR TROPICAL BIOLOGY AND CONSERVATION  
\begingroup 
\setlength{\leftskip}{.2cm}

President (2021)  
President-Elect (2020)  
Program Committee, Annual Meeting of the ATBC (2021)    
Student Field Grants Selection Committee (2020)  
Student Field Grants Selection Committee (2020)  
Crowdfunding Workshop, Annual Meeting of the ATBC (2018)  
Annual Meeting Scientific Committee (2017, 2012)  
Councillor (2009-2011)  
Conservation Committee (2004-2006)  
Co-organizer, Symposium on Amazonian Conservation, Annual Meeting (2004)  

\endgroup 

### SERVICE AS A REVIEWER AND EDITOR  

\begingroup 
\setlength{\leftskip}{.2cm}

*__Biotropica:__* Editor-in-Chief (2013-2019), Associate Editor (2010-2013), Editorial Board (2007-2019)  

*__Ecology__*, *__Ecological Monographs__*, and *__Ecological Applications__*: Editorial Board (2008-2012)  

__*Ad hoc* referee for journals (No. of reviews):__ *Trends in Ecology and Evolution* (1), *Nature Human Behavior* (1), *Information, Communication,& Society* (1), *Ecology* (4), *Ecology and Evolution* (1),  *Methods in Ecology & Evolution* (1), *Conservation Biology* (5), *Biological Conservation* (7), *Ecological Applications* (1), *Oecologia* (4), *Journal of Tropical Ecology* (2), *Journal of Ecology* (6), *New Phytologist* (1), *American Naturalist* (3), *Plant Ecology* (3), *Proc. Roy. Soc. Lond. B* (1), *Journal of Applied Ecology* (1), *Biotropica* (12), *Ecography* (5), *Ciência y Cultura* (2), *Oikos* (1), *Revista Chilena de Historia Natural* (1), *Biochemical Systematics & Ecology* (1), *Ecology Letters* (2), *Insectes Sociaux* (1), *American J. of Botany* (1), *Scientometrics* (1), *F1000* (1), *Desenvolvimento e Meio Ambiente* (1), *PLoS Biology* (2), *PLoS ONE* (1), *Theoretical Ecology* (1), *Conservation Science & Practice* (1)

__US National Science Foundation:__ Proposal Review Panels: DEB Ecology (2005), DEB Population and Evolutionary Processes (2007), DEB Population and Community Ecology (2011, 2013). Ad-hoc proposal review: UMEB Program (2), RUI Program (1), Ecological Biology Program (3), AMERICAS Dissertation Improvement Grant (1), NSF Global Scientists and Engineers Program (1), Population and Evolutionary Processes Program (1), International Research Fellowship Program (1), Population and Community Ecology Program (2), Dimensions of Biodiversity Program (1)

__Other service as a reviewer (No. of reviews or year of service)__: *Red Line Editorial (2019, technical review of a K-12 book), Mindlin Foundation (2018), Cornell University Press (2017), Instituto Serrapliheira (2017), HHMI Professors Program (2017), UF FAES/CRIS Project Proposals (2), U. of Chicago Press (1), Alfred P. Sloan Foundation Minority Ph.D. Program (3). National Geographic Society (1), U. of California Press (1)  

\endgroup 
### INVITED PRESENTATIONS
```{r talks, echo=FALSE,message = FALSE,warning=FALSE}
talks<-read_csv("./cv_files/talks.csv") %>% select(-year) %>% replace_na(list(year2=""))
kbl(talks, 
      format    = "latex", 
      align = "l",
      longtable = T, 
      row.names = FALSE,
      col.names = NULL,
      booktabs=T,
      linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)

```

### INTERVIEWS & MEDIA APPEARANCES  
\begingroup 
\setlength{\leftskip}{.2cm}

2021\hspace{4mm} Chronicle for Higher Education, The Florida Independent Alligator, Associated Press, Nightline (ABC)  
2020\hspace{4mm} Washington Post   
2019\hspace{4mm} USA Today, CBC News Network (Canada), The Atlantic, The Verge, MSNBC’s Velshi & Ruhle  
&nbsp;\hspace{10mm} WIRED Magazine (2), Mashable, BBC World Service (UK), The Miradas Podcast    
2018\hspace{4mm} Popular Science, Associated Press, National Geographic, Scholastic Classroom Magazines   
&nbsp;\hspace{10mm} Gainesville Sun, Mongabay.com  
2017\hspace{4mm} The Wire (India), Chemistry World, Nature, Gainesville Sun  
2016\hspace{4mm} Chronicle of Higher Education, DailyDot, Nature, Mongabay.com  
2014\hspace{4mm} NPR’s Morning Edition/Joe’s Big Idea, TV Acre (Rede Globo Rio Branco) Bom Dia Amazônia   
&nbsp;\hspace{10mm} TV Gazetta ‘Entrevista com Rogério Wenceslau’ (Rede Record Rio Branco), Estado de São Paulo  
&nbsp;\hspace{10mm} Nature.com, WUFT, Science/Science Insider, Howler Soccer Magazine’s Dummy Podcast  
2013\hspace{4mm} SciDevNet, WSLR Florida-Caribe Radio Show  
2006\hspace{4mm} The Scientist Magazine, Science Minority Scientists Network  
2005\hspace{4mm} Science’s Next Wave, Televisão Universitária, Uberlândia, Folha de São Paulo  
2004\hspace{4mm} Science Magazine’s Minority Scientists Network  
2002\hspace{4mm} NPR’s Weekend Edition Saturday, BBC World Service Radio 4, Austrian Public Television’s Modern Times. 

\endgroup

### PROFESSIONAL DEVELOPMENT  
\begingroup 
\setlength{\leftskip}{.2cm}  

2013\hspace{4mm} University of Florida Science Communication Academy  
2004\hspace{4mm} California Academy of Sciences: The Ant Course: Taxonomy & Systematics (Costa Rica)  
1996\hspace{4mm} Organization for Tropical Studies: Tropical Plant Systematics 96-9 (Costa Rica)  
1993\hspace{4mm} University of California Education Abroad Program: Tropical Biology Quarter (Costa Rica) 

\endgroup

### MEMBERSHIPS IN PROFESSIONAL SOCIETIES  

\begingroup 
\setlength{\leftskip}{.2cm}  
Ecological Society of America  
Association for Tropical Biology and Conservation
British Ecological Society  
American Association for the Advancement of Science  
International Society for Scientometrics and Infometrics  

\endgroup
