---
title: "Curriculum Vitae"
# title: "&nbsp;"
author: "Emilio M. Bruna"
email: embruna@ufl.edu
web: www.BrunaLab.org
github: embruna
twitter: BrunaLab
phone: "(352) 514-3935"
date: "`r format(Sys.time(), '%B %Y')`"
geometry: margin=.9in
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
# tables: true
# jobtitle: "Professor & Distinguished Teaching Scholar, University of Florida"
# address: "PO Box 110430 · 110 Newins-Ziegler Hall · Gainesville, FL 32611-040"
fontawesome: yes
bibliography: ./emb_cv_modular/EMB_publications.bib  
csl: brunacv.csl
# bibliography: BrunaPublications.bib
# bibliography: ./cv_files/BrunaPublications.bib
# bibliography_software: chapters.bib
# csl: biotropica.csl
# csl: ./cv_files/brunacv2.csl
updated: yes
# site: bookdown::bookdown_site
header-includes:
- \usepackage{etaremune} # for reverse-numbered list of publications etc
- \usepackage[default]{sourcesanspro}
- \usepackage{fancyhdr} # modify header into left, center, right
- \pagestyle{fancy} # cues the use of fancy headers
- \fancyfoot{} # cues the use of fancy footer
- \fancyfoot[R]{`r format(Sys.time(), '%B %Y')`} # month & year on footer right
- \fancyhead[R]{Emilio M. Bruna, p. \thepage} # name and page on header right
- \usepackage{setspace} # manipulate line spacing 
- \usepackage{parskip} # manipulate indents and spacing before/after paragraphs 
- \usepackage{xcolor} # changes colors of text
- \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  # to center to top level (#) headings (my name) and change color of font
  # more info # https://www.ctan.org/pkg/sectsty
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
# to center to sub-sub-headings (###) and change color of font
- \usepackage{sectsty} \subsubsectionfont{\color{darkmidnightblue}}
# http://latexcolor.com/ to choose colors
# define the colors used above with rgb codes
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
- \usepackage{xhfill}
# - \usepackage{ragged2e}
# # - \setlength\RaggedRightParindent{15pt}
# - \RaggedRight - # make the right margin ragged
# https://tex.stackexchange.com/questions/258714/prevent-hyphenation-across-lines-enforce-right-margin
# - \hyphenpenalty=10000 #to suppress ordinary hyphenation
# - \exhyphenpenalty=10000 #to prohibit line breaks at explicit hyphens.
# - \setstretch{1.0}

# https://babichmorrowc.github.io/post/changing-fonts-in-rmarkdown-pdfs/

output:
   pdf_document: default
   html_document:
   df_print: paged
   toc: false
# 
# 
# 
#    # \printbibliography[type=book,title={Books only}]
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
# library(citr)
library(RefManageR)
```
<!-- this next line suppresses the header (line, name,  page number) on 1st page -->
<!-- \begin{document}. -->
\thispagestyle{empty}  
# EMILIO MIGUEL BRUNA
\vspace{-0.3cm}  <!--space between name and address -->
University of Florida\hfill embruna@ufl.edu  
Dept. of Wildlife Ecology & Conservation &\hfill +1 (352) 846-0634  
Center for Latin American Studies\hfill&nbsp;[www.brunalab.org](www.brunalab.org)  
Gainesville, FL 32611-0430 USA\hfill&nbsp;[\@BrunaLab](https://twitter.com/BrunaLab) 
\vspace{-0.5cm}  <!--there was too much space, so reduced it with minus: -Xcm -->
<!-- ___   -->
\par\noindent\rule{\textwidth}{0.4pt}
\textbf{\textcolor{darkmidnightblue}{RESEARCH \& TEACHING INTERESTS:}} Tropical ecology and conservation, plant population ecology, plant-animal interactions, scientometrics and bibliometrics, science & science policy in Latin America  

\textbf{\textcolor{darkmidnightblue}{LANGUAGES:}} Fluent in Spanish, English, and Portuguese  
\vspace{-0.6cm}  

<!-- ```{r, child=c('one.Rmd', 'two.Rmd')} -->
<!-- ``` -->

<!-- ```{r, child='one.Rmd'} -->
<!-- ``` -->

### EDUCATION
<!--to indent a block of stuff treat it as a 'group' and then set leftskip -->
<!--be sure to indicate where the group ends with \endgroup -->

\begingroup 
\setlength{\leftskip}{.2cm} 

<!-- ### EDUCATION \hrulefill\ -->
<!-- TEXT \hrulefill\ -->
<!-- Here is some text\xfill{1pt} \par -->
<!-- Here is some text\xfill{8pt} \par -->
<!-- Here is some text\xhrulefill{darkmidnightblue}{2pt}\par -->
<!-- Here is some text\xhrulefill{darkmidnightblue}{1ex}\par -->
<!-- HOW TO MAKE LINE COLOR SAME???? -->
<!-- https://tex.stackexchange.com/questions/32597/vertically-centered-horizontal-rule-filling-the-rest-of-a-line -->
<!-- \textbf{\textcolor{darkmidnightblue}{EDUCATION }}\xrfill[0.5ex]{0.5pt} -->

<!-- ### EDUCATION \hrulefill -->
2001\hspace{4mm} Ph.D. in Population Biology, University of California, Davis  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm}  _Dissertation Co-Advisors: Susan P. Harrison and Sharon Y. Strauss_   -->
1995\hspace{4mm} M.S. in Biology, University of California, San Diego  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm} _Thesis Advisor: Ted J. Case_   -->
1994\hspace{4mm} B.S. in Ecology, Behavior, & Evolution with a minor in Literature, University of California, San Diego  

\endgroup 

<!-- ```{r ed, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- ed<-read_csv("./cv_files/education.csv") %>% -->
<!-- replace_na(list(program=" ", school=" ",year=" ",degree=" ")) -->
<!-- ed$program<-gsub('","',", ",ed$program) -->
<!-- ed$school<-gsub('","',", ",ed$school) -->
<!-- kbl(ed, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->

<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # row_spec(0:0, bold = T) %>% -->
<!--   # # column_spec(2, width = "35em") %>% -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->
<!-- ``` -->

### PROFESSIONAL APPOINTMENTS
\begingroup 
\setlength{\leftskip}{.2cm} 

2013-Present\hspace{6mm}**Professor & Distinguished Teaching Scholar**, University of Florida  
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2022-2025\hspace{10mm}**Secretary**, Ecological Society of America  

2020-2021\hspace{10mm}**President**, Association for Tropical Biology and Conservation  

2012-2021\hspace{10mm}**Director**, Florida-Brazil Linkage Institute, University of Florida   
&nbsp;\hspace{24mm}Center for Latin American Studies, University of Florida  

2013-2019\hspace{10mm}**Editor-in-Chief**, _Biotropica_  

2014-2020\hspace{10mm}**Board of Directors**, Dryad Digital Data Repository  

2005-Present\hspace{6mm}**Adjunct Professor**, Universidade Federal de Uberlândia, Brazil  
&nbsp;\hspace{24mm}Graduate Program in Ecology and Natural Resource Conservation  

2007-2013\hspace{10mm}**Associate Professor**, University of Florida  
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2002-2007\hspace{10mm}**Assistant Professor**, University of Florida    
&nbsp;\hspace{24mm}Department of Wildlife Ecology & Conservation & Center for Latin American Studies  

2001-2002\hspace{10mm}**NSF Minority Postdoctoral Fellow**, Biological Dynamics of Forest Fragments Project  
&nbsp;\hspace{24mm}Instituto Nacional de Pesquisas da Amazônia-Smithsonian Institution  

\endgroup
<!-- ```{r positions, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- positions<-read_csv("./cv_files/positions.csv") %>% -->
<!-- replace_na(list(dates=" ", position=" ")) -->

<!-- # positions<-as.data.frame(positions) -->
<!-- # positions[1,1] <- cell_spec(positions[1, 1], "latex", bold = T)  -->
<!-- kbl(positions, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->

<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # row_spec(0:0, bold = T) %>% -->
<!--   # # column_spec(2, width = "35em") %>% -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->
<!-- ``` -->

\vspace{-0.2cm}
### AWARDS
<!-- ```{r awards, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- awards<-read_csv("./cv_files/fellowships.csv") %>%  -->
<!--   filter(cat=="award") %>%  -->
<!--   select(-cat) %>%  -->
<!--   arrange(desc(year)) -->
<!-- awards$prize<-gsub('","',",",awards$prize) -->
<!-- awards$prize<-gsub("for the","\nfor the",awards$prize) -->
<!-- # awards$prize<- linebreak(awards$prize,double_escape = F, linebreaker = "\\n") -->
<!-- kbl(awards, -->
<!--     digits = 1, -->
<!--     format = "latex", -->
<!--     align="l", -->
<!--     col.names = NULL, -->
<!--     longtable = T, -->
<!--     row.names = FALSE, -->
<!--     booktabs=T, -->
<!--     linesep = "") %>% -->
<!--   kable_styling(bootstrap_options = c("hover"), -->
<!--                 latex_options = c("scale_down"), -->
<!--                 full_width = F, -->
<!--                 font_size = 10, -->
<!--                 position = "left") %>% -->
<!--   # column_spec(2, width = "35em") %>%  -->
<!--   sub("\\\\toprule", "", .) %>% -->
<!--   sub("\\\\bottomrule", "", .) -->

<!-- ``` -->

\begingroup 
\setlength{\leftskip}{.2cm} 

2023\hspace{4mm}Fellow, American Association for the Advancement of Science
2020\hspace{4mm}Selected for Induction into Alpha Zeta (Faculty Affiliate, UF Chapter)    
2020\hspace{4mm}Roche Teaching Scholar, UF College of Agricultural and Life Sciences    
2016\hspace{4mm}Sigma Xi (Full Member, University of Florida Chapter)    
2014\hspace{4mm}Academy of Distinguished Teaching Scholars, University of Florida  
2012\hspace{4mm}Outstanding Paper Award, US Chapter of the International Association for Landscape Ecology  
2011\hspace{4mm}Graduate Advisor & Teacher of the Year, UF College of Agricultural and Life Sciences  
2009\hspace{4mm}University of Florida Research Foundation Professor  
2007\hspace{4mm}Julie S. Denslow Outstanding Article in _Biotropica_ Prize, Association for Tropical Biology & Conservation  
2005\hspace{4mm}UF International Educator of the Year (untenured faculty category)  
2003\hspace{4mm}Diversity Scholar, American Institute for Biological Sciences  
2002\hspace{4mm}John L. Harper Early Career Researcher Award, British Ecological Society  
1994\hspace{4mm}Ernest C. Mort Leadership Excellence Award, Revelle College, UC San Diego  
<!-- &nbsp;\quad\quad\quad\quad _for the year’s outstanding contribution to the field, published in any journal_   -->
<!-- &nbsp;\quad\quad\quad\quad _for the outstanding paper published in the journal Biotropica_   -->
<!-- &nbsp;\quad\quad\quad\quad _for the outstanding paper by a young investigator in the Journal of Ecology_ -->

\endgroup


### SELECTED GRANTS IN SUPPORT OF RESEARCH, TRAINING, & PROGRAM DEVELOPMENT (total >$5.5 million)  

\begingroup 
\setlength{\leftskip}{.2cm}  

1. Maxwell-Hanrahan Foundaiton. "Support for the ATBC Field Grant Program" ($10,000; PIs Emilio M. Bruna, Patricia Sampaio, Lucia Lohmann, 2022-2023)

1. Sloan Foundation. “Reinventing Field Courses” ($74,060; PI: E. M. Bruna, Co-PIs: R. McCleery, P. Antonenko, N. Attias, D. Barton, 2020-2021)

1. National Science Foundation. SG: Synergistic effects of forest fragmentation and droughts on tropical plant population dynamics ($199,904; PI: E. M. Bruna, Co-PIs: M. Uriarte, 2020-2022).

1. National Science Foundation. REU Supplement for "SG: Synergistic effects of forest fragmentation and droughts on tropical plant population dynamics ($14,400; PI: E. M. Bruna, Co-PIs: M. Uriarte, 2021).

1. National Science Foundation. “The role of the matrix in fragmented landscapes: experimental tests and novel theory ($548,058; PI: R. Fletcher, Co-PIs: E. M. Bruna, R. D. Holt, and B. Reichert, 2018-2023)  


\endgroup

<!-- ### GRANT PROPOSALS UNDER REVIEW or IN PREPARATION -->

### RELEVANT PEER-REVIEWED PUBLICATIONS, BOOK CHAPTERS, & CORRESPONDENCE (N = 110)

**_Note regarding coauthorship on publications by lab members:_** _I am not a coauthor on papers by lab members, including publications that result from side projects or thesis chapters, as I consider mentorship regarding study development and design, analyses, and manuscript preparation fundamental to my role as their advisor. A list of the publications by lab members on which I am not a coauthor can be found below._ 

1. Halpern, B. S., C. Boettiger, M. C. Dietze, *et al.* 2023. Priorities for synthesis research in ecology and environmental Science.” *Ecosphere* 14(1): e4342. https://doi.org/10.1002/ecs2.4342

1. 	Scott, E. R., M. Uriarte, and E. M. Bruna. 2022. Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments. **_Global Change Biology_** 28(2):463-479.  https://onlinelibrary.wiley.com/doi/full/10.1111/gcb.15900 **_Recipient of the Postdoctoral Excellence Award from the Ecological Society of America's Plant Population Ecology Section_**

1. Bruna, E.M., R Chazdon, TM Errington and BA Nosek. 2021. A proposal to advance theory and promote collaboration in tropical biology by supporting replications. **_Biotropica_**, 53:6-10.  

7. Brooks, ME, K Kristensen, MR Darrigo, P Rubim, M Uriarte, E Bruna, and BM Bolker. 2019. Statistical modeling of patterns in annual reproductive rates. **_Ecology_** 100 (7):e02706 [Ph.D. Thesis Chapter].  

13. Costa, AN, HL Vasconcelos, and EM Bruna. 2017. Biotic drivers of seedling establishment in Neotropical savannas: Selective granivory and seedling herbivory by leaf-cutter ants as an ecological filter. **_Journal of Ecology_** 105:132-141. [Ph. D. Thesis Chapter].    

19. Mundim, FM, and EM Bruna. 2016. Is there a temperate bias in our understanding of how climate change will alter plant- herbivore interactions? A meta- analysis of experimental studies. **_American Naturalist_** 188:S74-S89. [Ph. D. Thesis Chapter] _**Selected as WEC Department's 2016 “High Impact Publication”**_.    

9.	Whitlock, MC, JL Bronstein, EM Bruna, AM Ellison, CW Fox, MA McPeek, AJ Moore, MAF Noor, MD Rausher, LH Rieseberg, M G Ritchie, and RG Shaw. 2016. A balanced data archiving policy for long-term studies. **_Trends in Ecology and Evolution_** 31(2) 84-85 [Response to article].  

22. Bruna, EM, TJ Izzo, BD Inouye, and HL Vasconcelos. 2014. Effect of mutualist partner identity on plant demography. **_Ecology_** 95:3237-3243. **_Cover Article_**.  

27. Côrtes, MC, M Uriarte, MR Lemes, R Gribel, W John Kress, PE Smouse, and EM Bruna. 2013. Low plant density enhances gene dispersal in the Amazonian understory herb _Heliconia acuminata_. **_Molecular Ecology_** 22:5716-5729. [Ph. D. Thesis Chapter].  

28. Jurinitz, CF, AA de Oliveira, and EM Bruna. 2013. Abiotic and biotic influences on early-stage survival in two shade-tolerant tree species in Brazil's Atlantic forest. **_Biotropica_** 45:728-736.  [Ph. D. Thesis Chapter].  

35. Bruna, EM, and AS de Andrade. 2011. Edge effects on growth and biomass partitioning of an Amazonian understory herb (_Heliconia acuminata_; Heliconiaceae). **_American Journal of Botany_** 98:1727-1734.   

39.	Uriarte, M. Anciães, M. T.B. da Silva, P. Rubim, E. Johnson, and E. M. Bruna.  2011. Disentangling the drivers of reduced long-distance seed dispersal by birds in an experimentally fragmented  landscape.  **_Ecology_** 92(4): 924-93. **_2012 Outstanding Paper in Landscape Ecology, Int. Assoc. for Landscape Ecology - US Chapter_**.  

38. Gagnon, PR, EM Bruna, P Rubim, MR Darrigo, RC Littell, M Uriarte, and WJ Kress. 2011. Growth of an understory herb is chronically reduced in Amazonian forest fragments. **_Biological Conservation_** 144:830-835.  

42. Fiske, IJ, and EM Bruna. 2010. Alternative spatial sampling in studies of plant demography: Consequences for estimates of population growth rate. **_Plant Ecology_** 207:213-225. [Ph. D. Thesis Chapter].    

44. Iacona, GD, LK Kirkman, and EM Bruna. 2010. Effects of resource availability on seedling recruitment in a fire-maintained savanna. **_Oecologia_** 163:171-180.  [Ph. D. Thesis Chapter].  

45. Quitete Portela, RDC, EM Bruna, and FA Maes dos Santos. 2010. Demography of palm species in Brazil's Atlantic Forest: A comparison of harvested and unharvested species using matrix models. **_Biodiversity and Conservation_** 19:2389-2403. [Ph. D. Thesis Chapter].   

47. Ribeiro, MBN, EM Bruna, and W Mantovani. 2010. Influence of post-clearing treatment on the recovery of herbaceous plant communities in Amazonian secondary forests. **_Restoration Ecology_** 18:50-58.  [Ph. D. Thesis Chapter].  

48. Uriarte, M, EM Bruna, P Rubim, M Anciaes, and I Jonckheere. 2010. Effects of forest fragmentation on the seedling recruitment of a tropical herb: assessing seed vs. safe-site limitation. **_Ecology_** 91:1317-1328.

49. Bruna, EM, IJ Fiske, and MD Trager. 2009. Habitat fragmentation and plant populations: Is what we know demographically irrelevant? **_Journal of Vegetation Science_** 20:569-576.   

52. Côrtes, M, V Gowda, WJ Kress, EM Bruna, and M Uriarte. 2009. Characterization of 10 microsatellite markers for the understory Amazonian herb _Heliconia acuminata_. **_Molecular Ecology Resources_** 9 1261-1264.  [Ph. D. Thesis Chapter].  

59. Fiske, IJ, EM Bruna, and BM Bolker. 2008. Effects of sample size on estimates of population growth rates calculated with matrix models. **_PLoS ONE_** 3:e3080.  [Ph. D. Thesis Chapter].  

63. De Athayde, SF, GM Da Silva, J Kaiabi, M Kaiabi, HR De Souza, K Ono, and EM Bruna. 2006. Participatory research and management of Arumã (_Ischnosiphon gracilis_ Rudge Koern., Marantaceae) by the Kaiabi people in the Brazilian Amazon. **_Journal of Ethnobiology_** 26:36-59. **_Cover article_**.  

67. Bruna, EM, and MBN Ribeiro. 2005. Regeneration and population structure of _Heliconia acuminata_ in Amazonian secondary forests with contrasting land-use histories. **_Journal of Tropical Ecology_** 21:127-131.  

68. Bruna, EM, and MK Oli. 2005. Demographic effects of habitat fragmentation on a tropical herb: Life-table response experiments. **_Ecology_** 86:1816-1824.  

69. Bruna, EM, and MBN Ribeiro. 2005. The compensatory responses of an understory herb to experimental damage are habitat-dependent. **_American Journal of Botany_** 92:2101-2210.    

74. Bruna, EM, WJ Kress, F Marques, and OF da Silva. 2004. _Heliconia acuminata_ reproductive success is independent of local floral density. **_Acta Amazonica_** 34:467-471. **_Cover Article_**.  

76. Nakazono, EM, EM Bruna, and RCG Mesquita. 2004. Experimental harvesting of the non-timber forest product _Ischnosiphon polyphyllus_ in central Amazonia. **_Forest Ecology and Management_** 190:219-225.  

77. Bruna, EM. 2003. Are plant populations in fragmented habitats recruitment limited? Tests with an Amazonian herb. **_Ecology_** 84:932-947.  

79. Bruna, EM. 2002. Effects of forest fragmentation on _Heliconia acuminata_ seedling recruitment in central Amazonia. **_Oecologia_** 132:235-243.  

80. Bruna, EM, and WJ Kress. 2002. Habitat fragmentation and the demographic structure of an Amazonian understory herb ( _Heliconia acuminata_). **_Conservation Biology_** 16:1256-1266.  

81. Bruna, EM, O Nardy, SY Strauss, and SP Harrison. 2002. Experimental assessment of _Heliconia acuminata_ growth in a fragmented Amazonian landscape. **_Journal of Ecology_** 90:639-649.  **_Recipient of the _John L. Harper Prize_ from the British Ecological Society_**.  

84. Bruna, EM. 1999. Seed germination in rainforest fragments. **_Nature_** 402:139.  


### SOFTWARE 

1. Fournier, A., F. Stevens, M. Boone, and E. M. Bruna. 2020. refsplitr. author name disambiguation, author georeferencing, and mapping of coauthorship networks with Web of Science data. R package version 1.0.0. https://github.com/ropensci/refsplitr

### COURSE DEVELOPMENT & TEACHING EXPERIENCE - UNIVERSITY OF FLORIDA
\begingroup 
\setlength{\leftskip}{.2cm}  
The Future of Rain Forests (Undergraduate, 2021, 2022)  
Data Collection & Management for Latin American Studies (Graduate, 2019, 2021, 2022)  
Ecology and Conservation of Tropical Wildlife (Undergraduate, 03,05,07,11,12,14,18)  
Plant-Animal Interactions (Graduate, 2004, 2006, 2008, 2010)  
Fundraising for Tropical Conservation & Development (Graduate, 2013, 2016, 2018, 2020)  
Scientific Publishing (Graduate, 2014, 2015, 2017, 2018)  
Ecological Principles for Development & Conservation Professionals (Graduate, 2010, 2011, 2012)  
Tropical Forest Community Ecology (Graduate, 2000)  
Design and Methods of Research in Latin American Studies (Graduate, 2008, 2010)  
Research Methods in Tropical Conservation & Development (Graduate, 2003-2007)  
Seminar in Wildlife Ecology and Conservation (Graduate, 2003, 2004)  
Social Media Workshop (Graduate, 2016)  
<!-- \endgroup  -->
<!-- \begingroup  -->
\setlength{\leftskip}{.2cm}  
<!-- __Other Teaching Experience__   -->
\endgroup 
### GRADUATE STUDENTS ADVISED
```{r GradStudentsA, echo=FALSE,message = FALSE,warning=FALSE}
# library(flextable)
# https://cran.r-project.org/web/packages/flextable/vignettes/format.html#borders
# df <- grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="advisor") %>% select(-role)
# table1<-df %>% regulartable() %>% autofit() %>% 
# width(j=~Degree,width=.3) %>% width(j=~Year,width=.9) %>% width(j=~Instititution,width=.1)
# table1 <- fontsize(table1, part = "header", size = 11) 
# table1 <- border_remove(x = table1)
# table1
```

```{r GradStudents, echo=FALSE,message = FALSE,warning=FALSE}
grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="advisor") %>% select(-role)
kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
    col.names = NULL,
    longtable = T,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
```

### POSTDOCTORAL, SABBATICAL, & POSTGRADUATE SCHOLARS 
```{r lab_members, echo=FALSE,message = FALSE,warning=FALSE}
lab_members<-read_csv("./cv_files/lab_members.csv") 
lab_members$cat<-as.factor(lab_members$cat)
lab_members$cat <- ordered(lab_members$cat, levels = c("postdoc","sab" ,"postgrad", "vis_grad","ug","hs"))
lab_members2<-lab_members %>% 
  filter(cat=="postdoc"|cat=="sab"|cat=="postgrad") %>% 
  arrange(order(cat)) %>% 
  select(-cat) %>% 
  drop_na()
  # replace_na(list(Name=" ", Institution=" ", Position=" ", Year=" "))
kbl(lab_members2,digits = 1,
    format = "latex",
    align="l",
    longtable = T, 
    col.names = NULL,
    row.names = FALSE,
    booktabs=T,
    linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
```

<!-- **Doctoral Defense Committee:** Helen Belan (U. Federal de Uberlândia, Brazil, 2020), Alan Nilo da Costa (U. Federal de Uberlândia, Brazil, 2013). **Doctoral Dissertation Examiner:** Talita Reis (UNICAMP, Brazil, 2015), Mauricio Bonesso Sampaio (UNICAMP, Brazil, 2012), Maria Rosa Darrigo (UNICAMP, Brazil, 2011), Sjirk Geerts (Stellenbosch University, South Africa, 2011), Rafael Soares de Arruda (INPA, Brazil, 2008), Thiago Junqueira Izzo (INPA, Brazil, 2005). **Doctoral Proposal Defense**: Laura Vivian Barbosa (U. Federal de Uberlândia, Brazil, 2014) **Master's Thesis Defense Committee**: Jonas B. Marvalhas (U. Federal de Uberlândia, Brazil 2013), Ernane Vieira Neto (U. Federal de Uberlândia, Brazil, 2008), Alan Nilo da Costa (U. Federal de Uberlândia, Brazil, 2007), Daniel Mascia Vieira (Universidade de Brasília, Brazil, 2002) -->

<!-- Carine Emer			INPA, Brazil				M.S. Thesis Examiner, 2011 -->
<!-- Flávio de Oliveira Rodrigues	INPA, Brazil				M.S. Thesis Examiner, 2011 -->
<!-- Waldete Castro Lourenço		INPA, Brazil				M.S. Thesis Examiner, 2009 -->
<!-- Simone B. Fontoura		INPA, Brazil				M.S. Thesis Examiner, 2007 -->
<!-- Paula M. Pedrosa			INPA, Brazil				M.S. Thesis Examiner, 2004 -->

<!-- Carine Emer 			INPA, Brazil				M.S. Proposal Examiner, 2009 -->
<!-- Simone Benedet Founatura	INPA, Brazil				M.S. Proposal Examiner, 2006 -->
<!-- Thiago Junqueira Izzo		INPA, Brazil				M.S. Proposal Examiner, 2002 -->

<!-- Melina Alcalá			UFSCar, Brazil				M.S. Qualifying Exam, 2009 -->
<!-- Raquel Negrão Baldoni		UFSCar, Brazil				M.S. Qualifying Exam, 2009 -->

<!-- Pedro B. Vasconcelos		U. Federal de Uberlândia, Brazil		B.S. Thesis Defense, 2009 -->
<!-- Fabiane M. Mundim 		U. Federal de Uberlândia, Brazil		B.S. Thesis Defense, 2007 -->

### UNDERGRADUATE THESIS STUDENTS, HIGH SCHOOL RESEARCHERS, & VISITING GRADUATE STUDENTS  
```{r lab_members2, echo=FALSE,message = FALSE,warning=FALSE}
lab_members<-read_csv("./cv_files/lab_members.csv") 
lab_members$cat<-as.factor(lab_members$cat)
lab_members$cat <- ordered(lab_members$cat, levels = c("postdoc","sab" ,"postgrad", "vis_grad","ug","hs"))
lab_members3<-lab_members %>% 
  filter(cat=="ug"|cat=="hs"|cat=="vis_grad") %>% 
  arrange(order(cat)) %>% 
  select(-cat) %>% 
  drop_na()
  # replace_na(list(Name=" ", Institution=" ", Position=" ", Year=" "))
kbl(lab_members3,digits = 1,
                  format = "latex",
                  align="l",
        longtable = T, 
    col.names = NULL,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
```

\begingroup 
\setlength{\leftskip}{.2cm}

*__Research Interns:__* _2007_: Wesley Dáttilo da Cruz, Univ. Estadual do Norte Fluminense (Brazil), Jefferson José Valsko da Silva, Universidade do Norte Fluminense (Brazil). _2005-2007_: Renata Pacheco do Nacimento and Cauê Thomé Lopes, Univ. Federal de Uberlândia (Brazil). _2005-2006_: Polyanna Custodio Duarte, Univ. Federal de Uberlândia (Brazil). _2006_: Waldete Castro Lourenço, Univ. Federal do Amazonas (Brazil), Elisabete Marques da Costa, Univ. Federal de Pernambuco (Brazil). _2005_: Bruno Turbiani, Universidade Estadual Paulista (Brazil). _2004_: Cristina Escate, Universidade Federal do Amazonas (Brazil), Simone Benedet, Universidade do Vale do Rio do Sinos (Brazil). _2003_: Cris Follman Jurinitz, Univ. Federal do Rio Grande do Sul (Brazil), Denise Cruz, Univ. Federal do Rio de Janeiro (Brazil). _2003-2004_: David M. Lapola, Universidade Estadual Paulista (Brazil). _2002_: Maria Beatriz Nogueira, Universidade de São Paulo (Brazil). _2001-2002_: Sylvia Heredia, Universidad de los Andes (Colombia). _2001_: Obed Garcia, INPA (Brazil), Olavo Nardy, UNESP (Brazil).

\endgroup

