---
title: "Curriculum Vitae - Modular"
# title: "&nbsp;"
author: "Emilio M. Bruna"
email: embruna@ufl.edu
web: www.BrunaLab.org
github: embruna
twitter: BrunaLab
phone: "(352) 514-3935"
date: "`r format(Sys.time(), '%B %Y')`"
geometry: margin=1in
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
fontawesome: yes
bibliography: EMB_publications.bib  
csl: brunacv.csl
updated: yes
header-includes:
- \usepackage{etaremune} # for reverse-numbered list of publications etc
- \usepackage[default]{sourcesanspro}
- \usepackage{fancyhdr} # modify header into left, center, right
- \pagestyle{fancy} # cues the use of fancy headers
- \fancyfoot{} # cues the use of fancy footer
- \fancyfoot[R]{`r format(Sys.time(), '%B %Y')`} # month & year on footer right
- \fancyhead[R]{Emilio M. Bruna, p. \thepage} # name and page on header right
- \usepackage{setspace} # manipulate line spacing 
- \usepackage{parskip} # manipulate indents and spacing before/after paragraphs 
- \usepackage{xcolor} # changes colors of text
- \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  # to center to top level (#) headings (my name) and change color of font
  # more info # https://www.ctan.org/pkg/sectsty
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
# to center to sub-sub-headings (###) and change color of font
- \usepackage{sectsty} \subsubsectionfont{\color{darkmidnightblue}}
# http://latexcolor.com/ to choose colors
# define the colors used above with rgb codes
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}

# - \setstretch{1.0}
# https://babichmorrowc.github.io/post/changing-fonts-in-rmarkdown-pdfs/
output:
   pdf_document: default
   html_document:
   df_print: paged
   toc: false
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
# library(citr)
library(RefManageR)
```

<!-- this next line suppresses the header (line, name,  page number) on 1st page -->
\thispagestyle{empty}

# EMILIO MIGUEL BRUNA

\vspace{-0.3cm}  <!--space between name and address -->

University of Florida\hfill embruna@ufl.edu  
Dept. of Wildlife Ecology & Conservation &\hfill +1 (352) 846-0634  
Center for Latin American Studies\hfill&nbsp;[www.brunalab.org](www.brunalab.org)  
Gainesville, FL 32611-0430 USA\hfill&nbsp;[\@BrunaLab](https://twitter.com/BrunaLab) 
\vspace{-0.5cm}  <!--there was too much space, so reduced it with minus: -Xcm -->

\par\noindent\rule{\textwidth}{0.4pt}

\textbf{\textcolor{darkmidnightblue}{RESEARCH \& TEACHING INTERESTS:}} Tropical ecology and conservation, plant population ecology, plant-animal interactions, scientometrics and bibliometrics, science & science policy in Latin America  

\textbf{\textcolor{darkmidnightblue}{LANGUAGES:}} Native fluency in Spanish and English, Fluent in Portuguese  
\vspace{-0.6cm}  

### EDUCATION

\begingroup 
\setlength{\leftskip}{.2cm} 

2001\hspace{4mm} Ph.D. in Population Biology, University of California, Davis  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm}  _Dissertation Co-Advisors: Susan P. Harrison and Sharon Y. Strauss_   -->
1995\hspace{4mm} M.S. in Biology, University of California, San Diego  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm} _Thesis Advisor: Ted J. Case_   -->
1994\hspace{4mm} B.S. in Ecology, Behavior, & Evolution with a minor in Literature, University of California, San Diego  

\endgroup 

<!-- Positions and Appointments -->
```{r, child='positions.Rmd'}
```

```{r, child='awards.Rmd'}
```

<!-- Fellowships -->
```{r, child='fellowships.Rmd'}
```

<!-- Grants (in review, granted, declined - comment out as needed -->
```{r, child='grants.Rmd'}
```


<!-- Peer reviewed Pubs -->
### PEER-REVIEWED ARTICLES, SOFTWARE, ESSAYS, AND OTHER PRODUCTS  

*Note: I do not co-author papers from my students’ theses unless I have made contributions substantially beyond the mentoring, fundraising, and editing I consider my fundamental responsibility as their advisor. Moreover, I encourage lab members to engage in side projects, which often result in publications on which I am not a co-author. A list of my lab members’ publications on which I am not a coauthor is below.* 

\begingroup 
\setlength{\leftskip}{.2cm}  
<!-- TODO: need to add in prep, software, etc. -->
 <!-- in YAML: \printbibliography[type=book,title={Books only}] -->
<div id="refs"></div> 
```{r, child='publications.Rmd'}
```
\endgroup

<!-- Teaching and Course Development -->
```{r, child='teaching.Rmd'}
```

<!-- my grad students -->
```{r, child='my_grad_students.Rmd'}
```

<!-- Member of PhD and MS Committees  -->
```{r, child='grad_student_committees.Rmd'}
```

<!-- Postdocs, Visitors, Interns -->
```{r, child='postdocs_visitors_interns.Rmd'}
```

<!-- Invited UF Service -->
```{r, child='service_uf.Rmd'}
```

<!-- Other Service (societies, reviewer & editorial services ) -->
```{r, child='service_other.Rmd'}
```

<!-- Invited Talks / Presentations -->
```{r, child='talks.Rmd'}
```

<!-- Intereviews & Media Appearances -->
```{r, child='media_appearances.Rmd'}
```

<!-- Professional Development -->
```{r, child='prof_development.Rmd'}
```

<!-- Society Memberships -->
```{r, child='society_memberships.Rmd'}
```






